---
title: Development of human lateral prefrontal sulcal morphology and its relation
  to reasoning performance
author: "EH Willbrand, E Ferrer, SA Bunge, & KS Weiner"
date: "4/5/2023"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message=FALSE)
```

#### Libraries

Requirements: packages below must be installed to load. 
```{r libraries}
# Unmark and run code below if packages are not installed
# project_packages <- c("tidyverse", "emmeans", "afex", "gt", "broom",
#                       "magrittr", "ggpubr", "factoextra", "NbClust",
#                       "ggnewscale", "reshape2", "lavaan", "nlme")
# install.packages(project_packages)

# Load packages 
## Data manipulation and plotting
library(tidyverse)
library(gt)
library(ggnewscale)
library(broom)
library(ggpubr)
library(magrittr)
library(factoextra)
library(reshape2)

## Statistics
library(NbClust)
library(emmeans)
library(afex)
library(lavaan)
library(nlme)

# Conditions for plots
dodge <- position_dodge(width = .9)
theme_set(theme_classic())
options(scipen = 999, show.signif.stars = FALSE) 
```


#### Morphological analysis: K-means clustering & MDS Analysis using four morphological features 
* K-means clustering of sulci using MDS data (based on depth, surface area, cortical thickness)
* Optimal number of clusters determined using NbClust (30 metrics)

##### Data
```{r, include = FALSE}
# set working directory to 'Development_PrefrontalSulci_Reasoning' folder  
setwd()

cross_sectional_devpfc_analysis <- read.csv("./data/morphological_analysis/crosssectional_data/cross_sectional_analysis_main.csv")
```

##### Figure 2A: MDS analyses & plots across groups
```{r}
### left hemisphere (lh)
#### set up data
cross_sectional_devpfc_analysis_lh <- cross_sectional_devpfc_analysis %>% subset(hemi == "lh") 
cross_sectional_devpfc_analysis_lh_morph <- cross_sectional_devpfc_analysis_lh %>%
  select(sulcal_depth_mm, total_surface_area_.mm.2., cortical_thickness_mean) 
cross_sectional_devpfc_analysis_lh_info <- cross_sectional_devpfc_analysis_lh %>% select(sub, hemi, label, age_group)
cross_sectional_devpfc_analysis_lh_scaled <- scale(cross_sectional_devpfc_analysis_lh_morph)
cross_sectional_devpfc_analysis_lh_scaled_info <- cbind(cross_sectional_devpfc_analysis_lh_info, cross_sectional_devpfc_analysis_lh_scaled)


#### mds
mds.lh.scaled <- cross_sectional_devpfc_analysis_lh_scaled %>% 
  dist() %>%
  cmdscale() 
colnames(mds.lh.scaled) <- c("Dim.1", "Dim.2")


#### determine best # of clusters
clust.analysis.lh <- NbClust(cross_sectional_devpfc_analysis_lh_scaled, distance = "euclidean", diss = NULL,
                  method = "kmeans", index = "all", min.nc = 2, max.nc = 9) 
# 11 proposed 2 as the best number of clusters; 8 proposed 5 

clust.analysis.lh.plt <- factoextra::fviz_nbclust(clust.analysis.lh) + 
  theme_minimal() + 
  ggtitle("NbClust's optimal number of clusters")


#### cluster based on optimal # of clusters = 3
set.seed(123)
clust.lh <- kmeans(mds.lh.scaled, 3)$cluster %>%
  as.factor()
mds.lh.scaled <- as.data.frame(mds.lh.scaled) %>%
  mutate(groups = clust.lh)


#### plot
mds.scaled.plt <- cbind(mds.lh.scaled, cross_sectional_devpfc_analysis_lh)

mds.scaled.plt <- mds.scaled.plt %>% mutate(groups2 = case_when(groups == 1 ~ "two",
                                                                groups == 2 ~ "one",
                                                                groups == 3 ~ "three"))

mds.lh.plt2 <- ggscatter(mds.scaled.plt, x = "Dim.1", y = "Dim.2", 
          size = 1,
          #shape = 21,
          color = "groups2",
          fill = "groups2",
          ellipse = TRUE,
          ellipse.type = "convex",
          repel = T) + 
  
  scale_color_manual(breaks = c("one","two", "three"), # "1","2", "3"
                     values = c("red",  "blue", "green")) +
  scale_fill_manual(breaks = c("one","two", "three"), # "1","2", "3"
                    values = c("red", "blue", "green")) +
  
  guides(fill = "none") +
  
  scale_x_continuous(n.breaks = 6, limits = c(-5, 5.5)) +
  scale_y_continuous(n.breaks = 6, limits = c(-3.5, 6.5)) +
  
  new_scale_fill() + 
  
  geom_point(aes(fill = label), 
             check_overlap = F, size = 1.5, shape = 21) +
  
  scale_fill_manual(breaks = c("central", 
                                  "sprs", "iprs", 
                                  "sfs_p", "sfs_a", 
                                  "imfs_h", "imfs_v",
                                  "pmfs_p", "pmfs_i", "pmfs_a", 
                                  "ifs",
                                  "half", "aalf", 
                                  "lfms", "prts", 
                                  "ts", "ds"),
                     values = c("#252525", # black
                                "#636363", "#cccccc", # gray
                                "#08306b", "#4292c6", # blues
                                "#66c2a4", "#b2e2e2", # teal
                                "#004529", "#4daf4a", "#addd8e", #greens
                                "#ffffff", # white
                                "#a50f15", "#de2d26", # reds
                                "darkorange3", "orange", # oranges
                                "yellow3", "yellow")) + # yellows 
  
  theme(
                        # set axis title
                        axis.title.x = element_text(color="#333333",
                                                    size=12), 
                        axis.title.y = element_text(color="#333333", 
                                                    angle=90,size=14),
                        # set axis text
                        axis.text = element_text( color='#333333',
                                                 size = 12),
                        # set pannel
                        
                        #panel.border = element_rect(colour = "black", 
                        #                fill=NA, size=1),
                        # set legend
                        legend.title = element_text(color="#333333",size = 12),
                        legend.text = element_text( color = '#333333',size = 12)
                        # set aspect ratio
                ) + 
  
  guides(fill = "none") 

# ggplot2::ggsave(filename = "~/Desktop/mds_lh_plt2.png",
#                  plot = mds.lh.plt2,
#                  device = "png",
#                  width = 8,
#                  height = 8, 
#                  units = "in",
#                  dpi = "retina")


### right hemisphere (rh)
#### set up data
cross_sectional_devpfc_analysis_rh <- cross_sectional_devpfc_analysis %>% subset(hemi == "rh") 
cross_sectional_devpfc_analysis_rh_morph <- cross_sectional_devpfc_analysis_rh %>%
  select(sulcal_depth_mm, total_surface_area_.mm.2., cortical_thickness_mean)
cross_sectional_devpfc_analysis_rh_info <- cross_sectional_devpfc_analysis_rh %>% select(sub, hemi, label, age_group)
cross_sectional_devpfc_analysis_rh_scaled <- scale(cross_sectional_devpfc_analysis_rh_morph)
cross_sectional_devpfc_analysis_rh_scaled_info <- cbind(cross_sectional_devpfc_analysis_rh_info, cross_sectional_devpfc_analysis_rh_scaled)


#### mds
mds.rh <- cross_sectional_devpfc_analysis_rh_scaled %>% 
  dist() %>%
  cmdscale() 
colnames(mds.rh) <- c("Dim.1", "Dim.2")


#### determine best # of clusters
nbclust.rh <- NbClust(mds_analysis_rh.scaled, distance = "euclidean",
                  method = "kmeans", index ="all", min.nc = 2, max.nc = 9) 
clust.analysis.rh.plt <- factoextra::fviz_nbclust(nbclust.rh) + theme_minimal() + ggtitle("NbClust's optimal number of clusters")


#### cluster based on optimal # of clusters = 3
set.seed(123)
clust.rh <- kmeans(mds.rh, 3)$cluster %>%
  as.factor()
mds.rh <- as.data.frame(mds.rh) %>%
  mutate(groups = clust.rh)


#### plot
mds.rh.scaled.plot <- cbind(mds.rh, cross_sectional_devpfc_analysis_rh)
mds.rh.scaled.plot <- mds.rh.scaled.plot %>% mutate(groups2 = case_when(groups == 1 ~ "one",
                                                                        groups == 2 ~ "three",
                                                                        groups == 3 ~ "two"))

mds.rh.plt <- ggscatter(mds.rh.scaled.plot, x = "Dim.1", y = "Dim.2", 
          size = 1,
          #shape = 21,
          color = "groups2",
          fill = "groups2",
          ellipse = TRUE,
          ellipse.type = "convex",
          repel = T) + 
  
  scale_color_manual(breaks = c("one","two", "three"), # "1","2", "3" "one","two", "three"
                     values = c("red",  "blue", "green")) +
  scale_fill_manual(breaks = c("one","two", "three"), # "1","2", "3"
                    values = c("red", "blue", "green")) +
  
  guides(fill = "none", color = "none") +
  
  scale_x_continuous(n.breaks = 6, limits = c(-5, 5.5)) +
  scale_y_continuous(n.breaks = 6, limits = c(-3.5, 6.5)) +
  
  new_scale_fill() + 
  
  geom_point(aes(fill = label), label = mds.rh.scaled.plot$label, check_overlap = F, size = 1.5, shape = 21) +
  
  scale_fill_manual(breaks = c("central", 
                                  "sprs", "iprs", 
                                  "sfs_p", "sfs_a", 
                                  "imfs_h", "imfs_v",
                                  "pmfs_p", "pmfs_i", "pmfs_a", 
                                  "ifs",
                                  "half", "aalf", 
                                  "lfms", "prts", 
                                  "ts", "ds"),
                     values = c("#252525", # black
                                "#636363", "#cccccc", # gray
                                "#08306b", "#4292c6", # blues
                                "#66c2a4", "#b2e2e2", # teal
                                "#004529", "#4daf4a", "#addd8e", #greens
                                "#ffffff", # white
                                "#a50f15", "#de2d26", # reds
                                "darkorange3", "orange", # oranges
                                "yellow3", "yellow")) + # yellows
  
  theme(
                        # set axis title
                        axis.title.x = element_text(color="#333333",
                                                    size=12), 
                        axis.title.y = element_text(color="#333333", 
                                                    angle=90,size=14),
                        # set axis text
                        axis.text = element_text( color='#333333',
                                                 size = 12),
                        # set pannel
                        
                        #panel.border = element_rect(colour = "black", 
                        #                fill=NA, size=1),
                        # set legend
                        legend.title = element_text(color="#333333",size = 12),
                        legend.text = element_text( color = '#333333',size = 12)
                        # set aspect ratio
                ) + 
  
  guides(fill = "none", color = "none") 

# ggplot2::ggsave(filename = "~/Desktop/mds_rh_plt.png",
#                  plot = mds.rh.plt,
#                  device = "png",
#                  width = 8,
#                  height = 8, 
#                  units = "in",
#                  dpi = "retina")

# plots for group counts
# mds.lh.group <- mds.scaled.plt %>% group_by(label, groups2) %>% summarise(n = n())
# mds.lh.group.plt <- ggplot(mds.lh.group, aes(x = label, y = n, fill = groups2)) + 
#   geom_col(color = 'black', size=.3, position = dodge) +                                                                                 
#   scale_fill_manual(breaks = c("one","two", "three"),
#                     values = c("red", "blue", "green")) + 
#                      coord_flip()

# mds.rh.group <- mds.rh.scaled.plot %>% group_by(label, groups) %>% summarise(n = n())
# mds.rh.group.plt <- ggplot(mds.rh.group, aes(x = label, y = n, fill = groups)) + 
#   geom_col(color = 'black', size=.3, position = dodge) + 
#   scale_fill_manual(breaks = c("1","2", "3"),
#                                 #, "3", "4", "5"),
#                      values = c("#e41a1c", "#377eb8", "#4daf4a")) + 
#   coord_flip()

# mds.both.scaled.plot <- rbind(mds.scaled.plt, mds.rh.scaled.plot)
# mds.group <- mds.both.scaled.plot %>% group_by(label, groups2) %>% 
#                                       summarise(n = n())
# mds.group.plt <- ggplot(mds.group, aes(x = label, y = n, fill = groups2)) + 
#   geom_col(color = 'black', size=.3, position = dodge) + 
#   scale_fill_manual(breaks = c("one","two", "three"),
#                    values = c("red", "blue", "green")) + 
#   coord_flip()
```

##### Figure 3: MDS analyses & plots by age group
```{r}
## lh children
cross_sectional_devpfc_analysis_lh_children <- cross_sectional_devpfc_analysis_lh_scaled_info %>% subset(age_group == "children")


### mds
mds_analysis.df.lh.children <- cross_sectional_devpfc_analysis_lh_children %>%
  select(sulcal_depth_mm, total_surface_area_.mm.2., cortical_thickness_mean) 
mds_analysis.df.lh.children.scaled <- scale(mds_analysis.df.lh.children)
mds.lh.children.scaled <- mds_analysis.df.lh.children.scaled %>% 
  dist() %>%
  cmdscale() 
colnames(mds.lh.children.scaled) <- c("Dim.1", "Dim.2")


### determine best # of clusters
clust.analysis.lh.children <- NbClust(mds_analysis.df.lh.children.scaled, distance = "euclidean", diss = NULL,
                  method = "kmeans", index = "all", min.nc = 2, max.nc = 9) 
set.seed(123)
clust_children.lh <- kmeans(mds.lh.children.scaled, 3)$cluster %>%
  as.factor()


### plot
mds.lh_children.scaled <- as.data.frame(mds.lh.children.scaled) %>%
  mutate(groups = clust_children.lh)
mds.scaled_children.plt <- cbind(mds.lh_children.scaled, cross_sectional_devpfc_analysis_lh_children)


mds.lh_children.group2 <- mds.scaled_children.plt %>% mutate(groups2 = case_when(groups == 1 ~ "one",
                                                                               groups == 2 ~ "two",
                                                                               groups == 3 ~ "three"))


mds.lh.plt2.children <- ggscatter(mds.lh_children.group2, x = "Dim.1", y = "Dim.2", 
          size = 1,
          #shape = 21,
          color = "groups",
          fill = "groups",
          ellipse = TRUE,
          ellipse.type = "convex",
          repel = T) + 
  
  scale_color_manual(breaks = c("1","2", "3"), # "1","2", "3" "one","two", "three"
                     values = c("red",  "blue", "green")) +
  scale_fill_manual(breaks = c("1","2", "3"), # "1","2", "3" "one","two", "three"
                    values = c("red", "blue", "green")) +
  
  guides(fill = "none") +
  
  scale_x_continuous(n.breaks = 6, limits = c(-5, 5.5)) +
  scale_y_continuous(n.breaks = 6, limits = c(-3.5, 6.5)) +
  
  new_scale_fill() + 
  
  geom_point(aes(fill = label), 
             check_overlap = F, size = 1.5, shape = 21) +
  
  scale_fill_manual(breaks = c("central", 
                                  "sprs", "iprs", 
                                  "sfs_p", "sfs_a", 
                                  "imfs_h", "imfs_v",
                                  "pmfs_p", "pmfs_i", "pmfs_a", 
                                  "ifs",
                                  "half", "aalf", 
                                  "lfms", "prts", 
                                  "ts", "ds"),
                     values = c("#252525", # black
                                "#636363", "#cccccc", # gray
                                "#08306b", "#4292c6", # blues
                                "#66c2a4", "#b2e2e2", # teal
                                "#004529", "#4daf4a", "#addd8e", #greens
                                "#ffffff", # white
                                "#a50f15", "#de2d26", # reds
                                "darkorange3", "orange", # oranges
                                "yellow3", "yellow")) + # yellows 
  
theme(
                        # set axis title
                        axis.title.x = element_text(color="#333333",
                                                    size=12), 
                        axis.title.y = element_text(color="#333333", 
                                                    angle=90,size=14),
                        # set axis text
                        axis.text = element_text( color='#333333',
                                                 size = 12),
                        # set pannel
                        
                        #panel.border = element_rect(colour = "black", 
                        #                fill=NA, size=1),
                        # set legend
                        legend.title = element_text(color="#333333",size = 12),
                        legend.text = element_text( color = '#333333',size = 12)
                        # set aspect ratio
                ) + 
  
  guides(fill = "none") 

# ggplot2::ggsave(filename = "~/Downloads/mds_lh_children.png",
#                  plot = mds.lh.plt2.children,
#                  device = "png",
#                  width = 8,
#                  height = 8, 
#                  units = "in",
#                  dpi = "retina")


# group counts lh
# mds.lh_children.group <- mds.scaled_children.plt %>% group_by(label, groups) %>% summarise(n = n())
# mds.lh_children.group.plt <- ggplot(mds.lh_children.group, aes(x = label, y = n, fill = groups)) + 
#   geom_col(color = 'black', size=.3, position = dodge) +                                                                            
#   scale_fill_manual(breaks = c("1","2", "3"),
#                     values = c("#e41a1c", "#377eb8", "#4daf4a")) + 
#                      coord_flip()


## rh children
cross_sectional_devpfc_analysis_rh_children <- cross_sectional_devpfc_analysis_rh_scaled_info %>% subset(age_group == "children")
mds_analysis.df.rh.children <- cross_sectional_devpfc_analysis_rh_children %>%
  select(sulcal_depth_mm, total_surface_area_.mm.2., cortical_thickness_mean) #, localGI)
mds_analysis.df.rh.children.scaled <- scale(mds_analysis.df.rh.children)

### mds
mds.rh.children.scaled <- mds_analysis.df.rh.children.scaled %>% 
  dist() %>%
  cmdscale() 
colnames(mds.rh.children.scaled) <- c("Dim.1", "Dim.2")


### determine best # of clusters
clust.analysis.rh.children <- NbClust(mds_analysis.df.rh.children.scaled, 
                                      distance = "euclidean", 
                                      diss = NULL,
                                      method = "kmeans", 
                                      index = "all",
                                      min.nc = 2, max.nc = 9) 
set.seed(123)
clust_children.rh <- kmeans(mds.rh.children.scaled, 3)$cluster %>%
  as.factor()
mds.rh_children.scaled <- as.data.frame(mds.rh.children.scaled) %>%
  mutate(groups = clust_children.rh)


### plot
mds.scaled_children.rh.plt <- cbind(mds.rh_children.scaled, cross_sectional_devpfc_analysis_rh_children)
mds.rh_children.group2 <- mds.scaled_children.rh.plt %>% mutate(groups2 = case_when(groups == 1 ~ "one",
                                                                               groups == 2 ~ "three",
                                                                               groups == 3 ~ "two"))


mds.rh.plt2.children <- ggscatter(mds.rh_children.group2, x = "Dim.1", y = "Dim.2", 
          size = 1,
          #shape = 21,
          color = "groups",
          fill = "groups",
          ellipse = TRUE,
          ellipse.type = "convex",
          repel = T) + 
  
  scale_color_manual(breaks = c("1","2", "3"), # "1","2", "3" "one","two", "three"
                     values = c("red",  "green", "blue")) +
  scale_fill_manual(breaks = c("1","2", "3"), # "1","2", "3"  "one","two", "three"
                    values = c("red", "green", "blue")) +
  
  guides(fill = "none") +
  
  scale_x_continuous(n.breaks = 6, limits = c(-5, 5.5)) +
  scale_y_continuous(n.breaks = 6, limits = c(-3.5, 6.5)) +
  
  new_scale_fill() + 
  
  geom_point(aes(fill = label), 
             check_overlap = F, size = 1.5, shape = 21) +
  
  scale_fill_manual(breaks = c("central", 
                                  "sprs", "iprs", 
                                  "sfs_p", "sfs_a", 
                                  "imfs_h", "imfs_v",
                                  "pmfs_p", "pmfs_i", "pmfs_a", 
                                  "ifs",
                                  "half", "aalf", 
                                  "lfms", "prts", 
                                  "ts", "ds"),
                     values = c("#252525", # black
                                "#636363", "#cccccc", # gray
                                "#08306b", "#4292c6", # blues
                                "#66c2a4", "#b2e2e2", # teal
                                "#004529", "#4daf4a", "#addd8e", #greens
                                "#ffffff", # white
                                "#a50f15", "#de2d26", # reds
                                "darkorange3", "orange", # oranges
                                "yellow3", "yellow")) + # yellows 
  
theme(
                        # set axis title
                        axis.title.x = element_text(color="#333333",
                                                    size=12), 
                        axis.title.y = element_text(color="#333333", 
                                                    angle=90,size=14),
                        # set axis text
                        axis.text = element_text( color='#333333',
                                                 size = 12),
                        # set pannel
                        
                        #panel.border = element_rect(colour = "black", 
                        #                fill=NA, size=1),
                        # set legend
                        legend.title = element_text(color="#333333",size = 12),
                        legend.text = element_text( color = '#333333',size = 12)
                        # set aspect ratio
                ) + 
  
  guides(fill = "none") 

# ggplot2::ggsave(filename = "~/Downloads/mds_rh_children.png",
#                  plot = mds.rh.plt2.children,
#                  device = "png",
#                  width = 8,
#                  height = 8, 
#                  units = "in",
#                  dpi = "retina")


# group counts rh
# mds.scaled_children.rh.plt.group <- mds.scaled_children.rh.plt %>% group_by(label, groups) %>% summarise(n = n())
# mds.rh_children.group.plt <- ggplot(mds.scaled_children.rh.plt.group, aes(x = label, y = n, fill = groups)) + 
#   geom_col(color = 'black', size=.3, position = dodge) +                                                                            
#   scale_fill_manual(breaks = c("1","2", "3"),
#                     values = c("#e41a1c", "#377eb8", "#4daf4a")) + 
#                      coord_flip()


# group counts combined
# mds.children.group2 <- rbind(mds.lh_children.group2, mds.rh_children.group2)
# mds.children.group2.combined <- mds.children.group2 %>% group_by(label, groups2) %>% summarise(n = n())
# 
# mds.children.group2.combined.plot <- ggplot(mds.children.group2.combined, aes(x = label, y = n, fill = groups2)) + 
#   geom_col(color = 'black', size=.3, position = dodge) +                                                                            
#   scale_fill_manual(breaks = c("one","two", "three"),
#                     values = c("#e41a1c", "#377eb8", "#4daf4a")) + 
#                     coord_flip()



## lh adolescent
cross_sectional_devpfc_analysis_lh_adolescent <- cross_sectional_devpfc_analysis_lh_scaled_info %>% subset(age_group == "adolescent")
mds_analysis.df.lh.adolescent <- cross_sectional_devpfc_analysis_lh_adolescent %>%
  select(sulcal_depth_mm, total_surface_area_.mm.2., cortical_thickness_mean) 
mds_analysis.df.lh.adolescent.scaled <- scale(mds_analysis.df.lh.adolescent)


### mds
mds.lh.adolescent.scaled <- mds_analysis.df.lh.adolescent.scaled %>% 
  dist() %>%
  cmdscale() 
colnames(mds.lh.adolescent.scaled) <- c("Dim.1", "Dim.2")


### determine best # of clusters
clust.analysis.lh.adolescent <- NbClust(mds_analysis.df.lh.adolescent.scaled, distance = "euclidean", diss = NULL,
                  method = "kmeans", index = "all",
                                      min.nc = 2, max.nc = 9) 
set.seed(123)
clust_ad.lh <- kmeans(mds.lh.adolescent.scaled, 3)$cluster %>%
  as.factor()
mds.lh.adolescent.scaled <- as.data.frame(mds.lh.adolescent.scaled) %>%
  mutate(groups = clust_ad.lh)


### plot
mds.scaled_ad.plt <- cbind(mds.lh.adolescent.scaled, cross_sectional_devpfc_analysis_lh_adolescent)
mds.lh_ad.group2 <- mds.scaled_ad.plt %>% mutate(groups2 = case_when(groups == 1 ~ "three",
                                                                       groups == 2 ~ "one",
                                                                       groups == 3 ~ "two"))

mds.lh.plt2.ad <- ggscatter(mds.lh_ad.group2, x = "Dim.1", y = "Dim.2", 
          size = 1,
          #shape = 21,
          color = "groups",
          fill = "groups",
          ellipse = TRUE,
          ellipse.type = "convex",
          repel = T) + 
  
  scale_color_manual(breaks = c("1","2", "3"), # "1","2", "3" "one","two", "three"
                     values = c("green",  "red", "blue")) +
  scale_fill_manual(breaks = c("1","2", "3"), # "1","2", "3" "one","two", "three"
                    values = c("green",  "red", "blue")) +
  
  guides(fill = "none") +
  
  scale_x_continuous(n.breaks = 6, limits = c(-5, 5.5)) +
  scale_y_continuous(n.breaks = 6, limits = c(-3.5, 6.5)) +
  
  new_scale_fill() + 
  
  geom_point(aes(fill = label), 
             check_overlap = F, size = 1.5, shape = 21) +
  
  scale_fill_manual(breaks = c("central", 
                                  "sprs", "iprs", 
                                  "sfs_p", "sfs_a", 
                                  "imfs_h", "imfs_v",
                                  "pmfs_p", "pmfs_i", "pmfs_a", 
                                  "ifs",
                                  "half", "aalf", 
                                  "lfms", "prts", 
                                  "ts", "ds"),
                     values = c("#252525", # black
                                "#636363", "#cccccc", # gray
                                "#08306b", "#4292c6", # blues
                                "#66c2a4", "#b2e2e2", # teal
                                "#004529", "#4daf4a", "#addd8e", #greens
                                "#ffffff", # white
                                "#a50f15", "#de2d26", # reds
                                "darkorange3", "orange", # oranges
                                "yellow3", "yellow")) + # yellows 
  
theme(
                        # set axis title
                        axis.title.x = element_text(color="#333333",
                                                    size=12), 
                        axis.title.y = element_text(color="#333333", 
                                                    angle=90,size=14),
                        # set axis text
                        axis.text = element_text( color='#333333',
                                                 size = 12),
                        # set pannel
                        
                        #panel.border = element_rect(colour = "black", 
                        #                fill=NA, size=1),
                        # set legend
                        legend.title = element_text(color="#333333",size = 12),
                        legend.text = element_text( color = '#333333',size = 12)
                        # set aspect ratio
                ) + 
  
  guides(fill = "none") 

# ggplot2::ggsave(filename = "~/Downloads/mds_lh_ad.png",
#                  plot = mds.lh.plt2.ad,
#                  device = "png",
#                  width = 8,
#                  height = 8, 
#                  units = "in",
#                  dpi = "retina")


# group counts lh
# mds.lh_ad.group <- mds.scaled_ad.plt %>% group_by(label, groups) %>% summarise(n = n())
# mds.lh_ad.group.plt <- ggplot(mds.lh_ad.group, aes(x = label, y = n, fill = groups)) + 
#   geom_col(color = 'black', size=.3, position = dodge) +   
#   scale_fill_manual(breaks = c("1","2", "3"),
#                     values = c("#e41a1c", "#377eb8", "#4daf4a")) + 
#                      coord_flip()


### rh adolescent 
cross_sectional_devpfc_analysis_rh_adolescent <- cross_sectional_devpfc_analysis_rh_scaled_info %>% subset(age_group == "adolescent")
mds_analysis.df.rh.adolescent <- cross_sectional_devpfc_analysis_rh_adolescent %>%
  select(sulcal_depth_mm, total_surface_area_.mm.2., cortical_thickness_mean) 
mds_analysis.df.rh.adolescent.scaled <- scale(mds_analysis.df.rh.adolescent)


### mds
mds.rh.adolescent.scaled <- mds_analysis.df.rh.adolescent.scaled %>% 
  dist() %>%
  cmdscale() 
colnames(mds.rh.adolescent.scaled) <- c("Dim.1", "Dim.2")


### determine best # of clusters
clust.analysis.rh.adolescent <- NbClust(mds_analysis.df.rh.adolescent.scaled, distance = "euclidean", diss = NULL,
                  method = "kmeans", index = "all", min.nc = 2, max.nc = 9) 
set.seed(123)
clust_ad.rh <- kmeans(mds.rh.adolescent.scaled, 4)$cluster %>%
  as.factor()


### plot
mds.rh.adolescent.scaled <- as.data.frame(mds.rh.adolescent.scaled) %>%
  mutate(groups = clust_ad.rh)
mds.rh.scaled_ad.plt <- cbind(mds.rh.adolescent.scaled, cross_sectional_devpfc_analysis_rh_adolescent)
mds.rh_ad.group2 <- mds.rh.scaled_ad.plt %>% mutate(groups2 = case_when(groups == 1 ~ "two",
                                                                       groups == 2 ~ "four",
                                                                       groups == 3 ~ "three",
                                                                       groups == 4 ~ "one"))


mds.rh.plt2.ad <- ggscatter(mds.rh_ad.group2, x = "Dim.1", y = "Dim.2", 
          size = 1,
          #shape = 21,
          color = "groups",
          fill = "groups",
          ellipse = TRUE,
          ellipse.type = "convex",
          repel = T) + 
  
  scale_color_manual(breaks = c("1","2", "3", "4"), # "1","2", "3" "one","two", "three", "four"
                     values = c("blue",  "cyan", "green", "red")) +
  scale_fill_manual(breaks = c("1","2", "3", "4"), # "1","2", "3" "one","two", "three", "four"
                    values = c("blue",  "cyan", "green", "red")) +
  
  guides(fill = "none") +
  
  scale_x_continuous(n.breaks = 6, limits = c(-5, 5.5)) +
  scale_y_continuous(n.breaks = 6, limits = c(-3.5, 6.5)) +
  
  new_scale_fill() + 
  
  geom_point(aes(fill = label), 
             check_overlap = F, size = 1.5, shape = 21) +
  
  scale_fill_manual(breaks = c("central", 
                                  "sprs", "iprs", 
                                  "sfs_p", "sfs_a", 
                                  "imfs_h", "imfs_v",
                                  "pmfs_p", "pmfs_i", "pmfs_a", 
                                  "ifs",
                                  "half", "aalf", 
                                  "lfms", "prts", 
                                  "ts", "ds"),
                     values = c("#252525", # black
                                "#636363", "#cccccc", # gray
                                "#08306b", "#4292c6", # blues
                                "#66c2a4", "#b2e2e2", # teal
                                "#004529", "#4daf4a", "#addd8e", #greens
                                "#ffffff", # white
                                "#a50f15", "#de2d26", # reds
                                "darkorange3", "orange", # oranges
                                "yellow3", "yellow")) + # yellows 
  
theme(
                        # set axis title
                        axis.title.x = element_text(color="#333333",
                                                    size=12), 
                        axis.title.y = element_text(color="#333333", 
                                                    angle=90,size=14),
                        # set axis text
                        axis.text = element_text( color='#333333',
                                                 size = 12),
                        # set pannel
                        
                        #panel.border = element_rect(colour = "black", 
                        #                fill=NA, size=1),
                        # set legend
                        legend.title = element_text(color="#333333",size = 12),
                        legend.text = element_text( color = '#333333',size = 12)
                        # set aspect ratio
                ) + 
  
  guides(fill = "none") 

# ggplot2::ggsave(filename = "~/Downloads/mds_rh_ad.png",
#                  plot = mds.rh.plt2.ad,
#                  device = "png",
#                  width = 8,
#                  height = 8, 
#                  units = "in",
#                  dpi = "retina")


# Group counts rh
# mds.rh_ad.group <- mds.rh.scaled_ad.plt %>% group_by(label, groups) %>% summarise(n = n())
# 
# mds.rh_ad.group.plt <- ggplot(mds.rh_ad.group, aes(x = label, y = n, fill = groups)) + 
#   geom_col(color = 'black', size=.3, position = dodge) +                                                                            
#   scale_fill_manual(breaks = c("1","2", "3"),
#                     values = c("#e41a1c", "#377eb8", "#4daf4a")) + 
#                      coord_flip()


# group counts both
# mds.ad.group2 <- rbind(mds.lh_ad.group2, mds.rh_ad.group2)
# mds.ad.group2.combined <- mds.ad.group2 %>% group_by(label, groups2) %>% summarise(n = n())
# 
# mds.rh_ad.group2.combined <- mds.rh_ad.group2 %>% group_by(label, groups) %>% summarise(n = n())
# 
# mds.rh_ad.group2.combined.plot <- ggplot(mds.rh_ad.group2.combined, aes(x = label, y = n, fill = groups)) + 
#   geom_col(color = 'black', size=.3, position = dodge) +                                                                            
#   scale_fill_manual(breaks = c("1","2", "3", "4"),
#                     values = c("blue",  "cyan", "green", "red")) + 
#                      coord_flip()



## lh young adult
cross_sectional_devpfc_analysis_lh_young_adult <- cross_sectional_devpfc_analysis_lh_scaled_info %>% subset(age_group == "young adult")
mds_analysis.df.lh.young_adult <- cross_sectional_devpfc_analysis_lh_young_adult %>%
  select(sulcal_depth_mm, total_surface_area_.mm.2., cortical_thickness_mean) 
mds_analysis.df.lh.young_adult.scaled <- scale(mds_analysis.df.lh.young_adult)


### mds
mds.lh.young_adult.scaled <- mds_analysis.df.lh.young_adult.scaled %>% 
  dist() %>%
  cmdscale() 
colnames(mds.lh.young_adult.scaled) <- c("Dim.1", "Dim.2")


### determine best # of clusters
clust.analysis.lh.young_adult <- NbClust(mds_analysis.df.lh.young_adult.scaled, distance = "euclidean", diss = NULL,
                  method = "kmeans", index = "all", min.nc = 2, max.nc = 9) 
set.seed(123)
clust_ya.lh <- kmeans(mds.lh.young_adult.scaled, 4)$cluster %>%
  as.factor()


### plot
mds.lh.young_adult.scaled <- as.data.frame(mds.lh.young_adult.scaled) %>%
  mutate(groups = clust_ya.lh)
mds.scaled_young_adult.plt <- cbind(mds.lh.young_adult.scaled, cross_sectional_devpfc_analysis_lh_young_adult)
mds.lh_young_adult.group2 <- mds.scaled_young_adult.plt %>% mutate(groups2 = case_when(groups == 1 ~ "two",
                                                                                       groups == 2 ~ "one",
                                                                                       groups == 3 ~ "three"))
mds.scaled_young_adult.plt$Dim.1.rev <- mds.scaled_young_adult.plt$Dim.1*-1

mds.lh.plt2.ya <- ggscatter(mds.scaled_young_adult.plt, x = "Dim.1.rev", y = "Dim.2", 
          size = 1,
          #shape = 21,
          color = "groups",
          fill = "groups",
          ellipse = TRUE,
          ellipse.type = "convex",
          repel = T) + 
  
  scale_color_manual(breaks = c("1","2", "3", "4"), # "1","2", "3" "one","two", "three", "four"
                     values = c("blue",  "brown1", "green", "darkred")) +
  scale_fill_manual(breaks = c("1","2", "3", "4"), # "1","2", "3"
                    values = c("blue",  "brown1", "green", "darkred")) +
  
  guides(fill = "none") +
  
  scale_x_continuous(n.breaks = 6, limits = c(-5, 5.5)) +
  scale_y_continuous(n.breaks = 6, limits = c(-3.5, 6.5)) +
  
  new_scale_fill() + 
  
  geom_point(aes(fill = label), 
             check_overlap = F, size = 1.5, shape = 21) +
  
  scale_fill_manual(breaks = c("central", 
                                  "sprs", "iprs", 
                                  "sfs_p", "sfs_a", 
                                  "imfs_h", "imfs_v",
                                  "pmfs_p", "pmfs_i", "pmfs_a", 
                                  "ifs",
                                  "half", "aalf", 
                                  "lfms", "prts", 
                                  "ts", "ds"),
                     values = c("#252525", # black
                                "#636363", "#cccccc", # gray
                                "#08306b", "#4292c6", # blues
                                "#66c2a4", "#b2e2e2", # teal
                                "#004529", "#4daf4a", "#addd8e", #greens
                                "#ffffff", # white
                                "#a50f15", "#de2d26", # reds
                                "darkorange3", "orange", # oranges
                                "yellow3", "yellow")) + # yellows 
  
theme(
                        # set axis title
                        axis.title.x = element_text(color="#333333",
                                                    size=12), 
                        axis.title.y = element_text(color="#333333", 
                                                    angle=90,size=14),
                        # set axis text
                        axis.text = element_text( color='#333333',
                                                 size = 12),
                        # set pannel
                        
                        #panel.border = element_rect(colour = "black", 
                        #                fill=NA, size=1),
                        # set legend
                        legend.title = element_text(color="#333333",size = 12),
                        legend.text = element_text( color = '#333333',size = 12)
                        # set aspect ratio
                ) + 
  
  guides(fill = "none") 

# ggplot2::ggsave(filename = "~/Downloads/mds_lh_ya.png",
#                  plot = mds.lh.plt2.ya,
#                  device = "png",
#                  width = 8,
#                  height = 8, 
#                  units = "in",
#                  dpi = "retina")


# group counts lh
# mds.lh_ya.group <- mds.scaled_young_adult.plt %>% group_by(label, groups) %>% summarise(n = n())
# mds.lh_ya.group.plt <- ggplot(mds.lh_ya.group, aes(x = label, y = n, fill = groups)) + 
#   geom_col(color = 'black', size=.3, position = dodge) +                                                                            
#   scale_fill_manual(breaks = c("1","2", "3"),
#                     values = c("#e41a1c", "#377eb8", "#4daf4a")) + 
#                      coord_flip()


## rh young adults
cross_sectional_devpfc_analysis_rh_young_adult <- cross_sectional_devpfc_analysis_rh_scaled_info %>% subset(age_group == "young adult")
mds_analysis.df.rh.young_adult <- cross_sectional_devpfc_analysis_rh_young_adult %>%
  select(sulcal_depth_mm, total_surface_area_.mm.2., cortical_thickness_mean)
mds_analysis.df.rh.young_adult.scaled <- scale(mds_analysis.df.rh.young_adult)


### mds
mds.rh.young_adult.scaled <- mds_analysis.df.rh.young_adult.scaled %>% 
  dist() %>%
  cmdscale() 
colnames(mds.rh.young_adult.scaled) <- c("Dim.1", "Dim.2")


### determine best # of clusters
clust.analysis.rh.young_adult <- NbClust(mds_analysis.df.rh.young_adult.scaled, distance = "euclidean", diss = NULL,
                  method = "kmeans", index = "all", min.nc = 2, max.nc = 9) 
set.seed(123)
clust_ya.rh <- kmeans(mds.rh.young_adult.scaled, 4)$cluster %>%
  as.factor()


### plot
mds.rh.young_adult.scaled <- as.data.frame(mds.rh.young_adult.scaled) %>%
  mutate(groups = clust_ya.rh)
mds.rh_scaled_young_adult.plt <- cbind(mds.rh.young_adult.scaled, cross_sectional_devpfc_analysis_rh_young_adult)
mds.rh_young_adult.group2 <- mds.rh_scaled_young_adult.plt %>% mutate(groups2 = case_when(groups == 1 ~ "one",
                                                                                          groups == 2 ~ "three",
                                                                                          groups == 3 ~ "two"))
mds.rh_scaled_young_adult.plt$Dim.1.rev <- mds.rh_scaled_young_adult.plt$Dim.1*-1

mds.rh.plt2.ya <- ggscatter(mds.rh_scaled_young_adult.plt, x = "Dim.1.rev", y = "Dim.2", 
          size = 1,
          #shape = 21,
          color = "groups",
          fill = "groups",
          ellipse = TRUE,
          ellipse.type = "convex",
          repel = T) + 
  
  scale_color_manual(breaks = c("1","2", "3", "4"), # "1","2", "3" "one","two", "three", "four"
                     values = c("brown1",  "green", "blue", "darkred")) +
  scale_fill_manual(breaks = c("1","2", "3", "4"), # "1","2", "3"
                    values = c("brown1",  "green", "blue", "darkred")) +
  
  guides(fill = "none") +
  
  scale_x_continuous(n.breaks = 6, limits = c(-5, 5.5)) +
  scale_y_continuous(n.breaks = 6, limits = c(-3.5, 6.5)) +
  
  new_scale_fill() +
  
  geom_point(aes(fill = label), 
             check_overlap = F, size = 1.5, shape = 21) +
  
  scale_fill_manual(breaks = c("central", 
                                  "sprs", "iprs", 
                                  "sfs_p", "sfs_a", 
                                  "imfs_h", "imfs_v",
                                  "pmfs_p", "pmfs_i", "pmfs_a", 
                                  "ifs",
                                  "half", "aalf", 
                                  "lfms", "prts", 
                                  "ts", "ds"),
                     values = c("#252525", # black
                                "#636363", "#cccccc", # gray
                                "#08306b", "#4292c6", # blues
                                "#66c2a4", "#b2e2e2", # teal
                                "#004529", "#4daf4a", "#addd8e", #greens
                                "#ffffff", # white
                                "#a50f15", "#de2d26", # reds
                                "darkorange3", "orange", # oranges
                                "yellow3", "yellow")) + # yellows 
  
theme(
                        # set axis title
                        axis.title.x = element_text(color="#333333",
                                                    size=12), 
                        axis.title.y = element_text(color="#333333", 
                                                    angle=90,size=14),
                        # set axis text
                        axis.text = element_text( color='#333333',
                                                 size = 12),
                        # set pannel
                        
                        #panel.border = element_rect(colour = "black", 
                        #                fill=NA, size=1),
                        # set legend
                        legend.title = element_text(color="#333333",size = 12),
                        legend.text = element_text( color = '#333333',size = 12)
                        # set aspect ratio
                ) + 
  
  guides(fill = "none") 

# ggplot2::ggsave(filename = "~/Downloads/mds_rh_ya.png",
#                  plot = mds.rh.plt2.ya,
#                  device = "png",
#                  width = 8,
#                  height = 8, 
#                  units = "in",
#                  dpi = "retina")


# group counts rh
# mds.rh_ya.group <- mds.rh_scaled_young_adult.plt %>% group_by(label, groups) %>% summarise(n = n())
# mds.rh_ya.group.plt <- ggplot(mds.rh_ya.group, aes(x = label, y = n, fill = groups)) + 
#   geom_col(color = 'black', size=.3, position = dodge) +                                                                            
#   scale_fill_manual(breaks = c("1","2", "3"),
#                     values = c("#e41a1c", "#377eb8", "#4daf4a")) + 
#                      coord_flip()


# group counts both
# mds.ya.group2 <- rbind(mds.lh_young_adult.group2, mds.rh_young_adult.group2)
# mds.ya.group2.combined <- mds.ya.group2 %>% group_by(label, groups2) %>% summarise(n = n())
# mds.ya.group2.combined.plot <- ggplot(mds.ya.group2.combined, aes(x = label, y = n, fill = groups2)) + 
#   geom_col(color = 'black', size=.3, position = dodge) +                                                                            
#   scale_fill_manual(breaks = c("one","two", "three"),
#                     values = c("#e41a1c", "#377eb8", "#4daf4a")) + 
#                      coord_flip()
```

##### Cluster sulci by group majority for cross-sectional analyses
```{r}
group_dev_analysis <- cross_sectional_devpfc_analysis %>% mutate(sulcal_cluster = 
                                  
                                    case_when(label %in% c("central", "iprs", "sprs", "ifs", "sfs_p") ~ "border",
                                              label %in% c("aalf", "ds", "ts") ~ "ventral", 
                                              label %in%  c("sfs_a", "imfs_v", "imfs_h",
                                              "pmfs_p", "pmfs_i", "pmfs_a", "prts", "lfms", "half") ~ "dorsal"
))

## describe features
group_dev_analysis %>% group_by(sulcal_cluster) %>% summarise(mean_depth = mean(sulcal_depth_mm),
                                                              mean_sa = mean(total_surface_area_.mm.2.),
                                                              mean_ct = mean(cortical_thickness_mean))

```


#### Morphological analysis: Cross-sectional age-group comparisons

##### Stats 1
* N-way (sulcal label x hemi x age group x gender) mixed model ANOVA to test for differences in depth, surface area, & cortical thickness (and normalized versions)

* Within-subject effects:
* sulcal group: DLPFC, VLPFC, and border sulci (only including interactions)
* hemi: lh, rh

* Between-subject effects:
* age_group: children, adolescent, young adult
* gender: male, female

###### Sulcal depth ANOVA
```{r}
# raw 
## anova
depth_model_raw <- afex::aov_ez(id = "sub", 
                            dv = "sulcal_depth_mm", 
                            within =c('hemi', 'sulcal_cluster'), 
                            between = c('age_group', 'gender'),
                            data = group_dev_analysis
)

## output
depth_model_raw_out <- depth_model_raw$anova_table
depth_model_raw_out$type <- "raw"
depth_model_raw_out$Effect <- rownames(depth_model_raw_out)

## contrasts
depth_model_raw.m1 <- emmeans::emmeans(depth_model_raw,'age_group')
emmeans::contrast(depth_model_raw.m1, method='pairwise')
group_dev_analysis %>% group_by(age_group) %>% summarise(mean_depth = mean(sulcal_depth_mm))


# normalized
## anova
depth_model_norm <- afex::aov_ez(id = "sub", 
                            dv = "depth_pct_max", 
                            within =c('hemi', 'sulcal_cluster'), 
                            between = c('age_group', 'gender'),
                            data = group_dev_analysis
)

## output
depth_model_norm_out <- depth_model_norm$anova_table
depth_model_norm_out$type <- "norm"
depth_model_norm_out$Effect <- rownames(depth_model_norm_out)

## contrasts
depth_model_norm.m1 <- emmeans::emmeans(depth_model_norm,'age_group')
emmeans::contrast(depth_model_norm.m1, method='pairwise')
group_dev_analysis %>% group_by(age_group) %>% summarise(mean_depth_pct_max = mean(depth_pct_max))


## combined output
depth_model_table <- rbind(depth_model_raw_out, depth_model_norm_out)
depth_model_table$metric <- "depth"
```

###### Surface area ANOVA
```{r}
# raw
## anova
surface_area_model_raw <- afex::aov_ez(id = "sub", 
                            dv = "total_surface_area_.mm.2.", 
                            within =c('hemi', 'sulcal_cluster'), 
                            between = c('age_group', 'gender'),
                            data = group_dev_analysis
)

## output
surface_area_model_raw_out <- surface_area_model_raw$anova_table
surface_area_model_raw_out$type <- "raw"
surface_area_model_raw_out$Effect <- rownames(surface_area_model_raw_out)


# normalized
## anova
surface_area_model_norm <- afex::aov_ez(id = "sub", 
                            dv = "sa_normed", 
                            within =c('hemi', 'sulcal_cluster'), 
                            between = c('age_group', 'gender'),
                            data = group_dev_analysis
)

## contrasts
sa_norm_model.i1 <- emmeans::emmeans(surface_area_model_norm, ~ age_group | sulcal_cluster)
emmeans::contrast(sa_norm_model.i1, method='pairwise')
group_dev_analysis %>% group_by(sulcal_cluster, age_group) %>% summarise(mean = mean(sa_normed))

## output
surface_area_model_norm_out <- surface_area_model_norm$anova_table
surface_area_model_norm_out$type <- "norm"
surface_area_model_norm_out$Effect <- rownames(surface_area_model_norm_out)


## combined output
surface_area_model_table <- rbind(surface_area_model_raw_out, surface_area_model_norm_out)
surface_area_model_table$metric <- "surface area"
```

###### Cortical thickness ANOVA
```{r}
# raw 
## anova
cortical_thickness_model_raw <- afex::aov_ez(id = "sub", 
                            dv = "cortical_thickness_mean", 
                            within =c('hemi', 'sulcal_cluster'), 
                            between = c('age_group', 'gender'),
                            data = group_dev_analysis
)

## output
cortical_thickness_model_raw_out <- cortical_thickness_model_raw$anova_table
cortical_thickness_model_raw_out$type <- "raw"
cortical_thickness_model_raw_out$Effect <- rownames(cortical_thickness_model_raw_out)

## contrast
cortical_thickness_model_raw.m1 <- emmeans::emmeans(cortical_thickness_model_raw, 'age_group')
emmeans::contrast(cortical_thickness_model_raw.m1, method='pairwise')
group_dev_analysis %>% group_by(age_group) %>% summarise(cortical_thickness_mean = mean(cortical_thickness_mean))


# normalized
## anova
cortical_thickness_model_norm <- afex::aov_ez(id = "sub", 
                            dv = "cortical_thickness_normed", 
                            within =c('hemi', 'sulcal_cluster'), 
                            between = c('age_group', 'gender'),
                            data = group_dev_analysis
)

## output
cortical_thickness_model_norm_out <- cortical_thickness_model_norm$anova_table
cortical_thickness_model_norm_out$type <- "norm"
cortical_thickness_model_norm_out$Effect <- rownames(cortical_thickness_model_norm_out)

## contrast
cortical_thickness_model_norm.m1 <- emmeans::emmeans(cortical_thickness_model_norm, 'age_group')
emmeans::contrast(cortical_thickness_model_norm.m1, method='pairwise')
group_dev_analysis %>% group_by(age_group) %>% summarise(mean_cortical_thickness_normed = mean(cortical_thickness_normed))


## combined output
cortical_thickness_model_table <- rbind(cortical_thickness_model_raw_out, cortical_thickness_model_norm_out)
cortical_thickness_model_table$metric <- "thickness"
```

###### FDR correction on ANOVAs
```{r}
# merge tables together
all_morph_tables <- rbind(depth_model_table, surface_area_model_table, cortical_thickness_model_table) #localGI_model_raw_table)
all_morph_tables <- all_morph_tables %>% select(-c("MSE"))

# conduct FDR correction
p_val_tst_adj <- p.adjust(p = all_morph_tables$`Pr(>F)`, 
                              method = "fdr")

# round values to be more readable
p_val_tst_adj <- round(as.data.frame(p_val_tst_adj), 3) # round

# adjustments to table

## merge adjusted with original
all_morph_tables <- cbind(all_morph_tables, p_val_tst_adj)

## round values to be more readable 
all_morph_tables$`num Df` <- round(all_morph_tables$`num Df`, 3)
all_morph_tables$`den Df` <- round(all_morph_tables$`den Df`, 3)
all_morph_tables$F <- round(all_morph_tables$F, 3)
all_morph_tables$ges <- round(all_morph_tables$ges, 3) 
all_morph_tables$p_val_tst_adj <- round(all_morph_tables$p_val_tst_adj, 3) 

## major adjustments 
all_morph_tables_f <- all_morph_tables %>% select(-c(5)) %>% 
  rename(p_value_adj = p_val_tst_adj, DF1 = `num Df`, DF2 = `den Df`) %>%
  mutate(significance = case_when(p_value_adj >= .1 ~ "", 
                                  p_value_adj < .1 & p_value_adj >= .05 ~ "+",
                                  p_value_adj < .05 & p_value_adj >= .01 ~ "*",
                                  p_value_adj < .01 & p_value_adj >= .001 ~ "**",
                                  p_value_adj < .001 ~ "***" 
                             )
  ) %>%
  mutate(p_value_adj = replace(p_value_adj, p_value_adj == 0.000, "< 0.001"))

col_order <- c("Effect", "DF1", "DF2", 
               "F", "p_value_adj", "significance", "ges", "type", "metric")
all_morph_tables_f <- all_morph_tables_f[, col_order]
```

##### Visualizations for Figure 4A, B, C and Extended Data Figure 4-1A, B, C: Cross-sectional results
```{r}
group_dev_analysis$age_group <- factor(group_dev_analysis$age_group, 
                                         levels = c("children", "adolescent", "young adult"))

# sulcal depth
## raw
lpfc_depth_plot <- ggplot(group_dev_analysis, aes(x = sulcal_cluster, y = sulcal_depth_mm)) + 
  
  geom_point(aes(y = sulcal_depth_mm, fill = age_group), 
              shape = 21, color = 'black', 
              alpha = .5, position = position_jitterdodge()
              ) + 
  
  geom_boxplot(aes(y = sulcal_depth_mm, fill = age_group),color = 'black',
               alpha = .6, position = position_dodge(width = 0.75),
               outlier.size = 0, outlier.alpha = 0,
               width = 0.5, size = .75) +
  
  scale_fill_manual(breaks = c("children", "adolescent", "young adult"),
                    values = c("#009E73", "#56B4E9", "#E69F00")
                    ) +
  
  labs(x = "cluster group",
       y = "sulcal depth (mm)") + 
  
  guides(fill = "none", color = "none", alpha = "none") +
  
  scale_y_continuous(n.breaks = 10) +
  
  theme_classic() +
  
  theme( 
                        # set axis title
                        axis.title.x = element_text(color="#333333",
                                                    size=12), 
                        axis.title.y = element_text(color="#333333", 
                                                    angle=90,size=14),
                        # set axis text
                        axis.text = element_text( color='#333333',
                                                 size = 12),
                        # set pannel
                        
                        #panel.border = element_rect(colour = "black", 
                        #                fill=NA, size=1),
                        # set legend
                        legend.title = element_text(color="#333333",size = 12),
                        legend.text = element_text( color = '#333333',size = 12),
                        # remove facet 
                        strip.background = element_blank(),
                        strip.text = element_text(size = 0)
                ) +
  
  facet_wrap( ~ hemi)
  
# ggplot2::ggsave(filename = "~/Downloads/lpfc_depth_plot.png",
#                  plot = lpfc_depth_plot,
#                  device = "png",
#                  width = 7,
#                  height = 7,
#                  units = "in",
#                  dpi = "retina")

## normalized
lpfc_depth_norm_plot <- ggplot(group_dev_analysis, aes(x = sulcal_cluster, y = depth_pct_max)) + 
  
  geom_point(aes(y = depth_pct_max, fill = age_group), 
              shape = 21, color = 'black', 
              alpha = .5, position = position_jitterdodge()
              ) + 
  
  geom_boxplot(aes(y = depth_pct_max, fill = age_group),color = 'black',
               alpha = .6, position = position_dodge(width = 0.75),
               outlier.size = 0, outlier.alpha = 0,
               width = 0.5, size = .75) +
  
  scale_fill_manual(breaks = c("children", "adolescent", "young adult"),
                    values = c("#009E73", "#56B4E9", "#E69F00")
                    ) +
  
  labs(x = "cluster group",
       y = "sulcal depth (mm)") + 
  
  guides(fill = "none", color = "none", alpha = "none") +
  
  scale_y_continuous(n.breaks = 10, limits = c(0:1)) +
  
  theme_classic() +
  
  theme( 
                        # set axis title
                        axis.title.x = element_text(color="#333333",
                                                    size=12), 
                        axis.title.y = element_text(color="#333333", 
                                                    angle=90,size=14),
                        # set axis text
                        axis.text = element_text( color='#333333',
                                                 size = 12),
                        # set pannel
                        
                        #panel.border = element_rect(colour = "black", 
                        #                fill=NA, size=1),
                        # set legend
                        legend.title = element_text(color="#333333",size = 12),
                        legend.text = element_text( color = '#333333',size = 12),
                        # remove facet 
                        strip.background = element_blank(),
                        strip.text = element_text(size = 0)
                ) +
  
  facet_wrap( ~ hemi)
  
# ggplot2::ggsave(filename = "~/Downloads/lpfc_depth_norm_plot.png",
#                  plot = lpfc_depth_norm_plot,
#                  device = "png",
#                  width = 7,
#                  height = 7,
#                  units = "in",
#                  dpi = "retina")


# surface area
## raw
lpfc_sa_plot <- ggplot(group_dev_analysis, aes(x = sulcal_cluster, y = total_surface_area_.mm.2./100)) +
  
  geom_point(aes(y = total_surface_area_.mm.2./100, fill = age_group), 
              shape = 21, color = 'black', 
              alpha = .5, position = position_jitterdodge()
              ) + 
  
  geom_boxplot(aes(y = total_surface_area_.mm.2./100, fill = age_group),color = 'black',
               outlier.size = 0, outlier.alpha = 0,
               alpha = .6, position = position_dodge(width = 0.75),
                width = 0.5, size = .75) +
  
  scale_fill_manual(breaks = c("children", "adolescent", "young adult"),
                    values = c("#009E73", "#56B4E9", "#E69F00")
                    ) +
  
  labs(x = "cluster group",
       y = "surface area (mm2)") + 
  
  guides(fill = "none", color = "none", alpha = "none") +
  
  scale_y_continuous(n.breaks = 10) +
  
  theme_classic() +
  
  theme( 
                        # set axis title
                        axis.title.x = element_text(color="#333333",
                                                    size=12), 
                        axis.title.y = element_text(color="#333333", 
                                                    angle=90,size=14),
                        # set axis text
                        axis.text = element_text( color='#333333',
                                                 size = 12),
                        # set pannel
                        
                        #panel.border = element_rect(colour = "black", 
                        #                fill=NA, size=1),
                        # set legend
                        legend.title = element_text(color="#333333",size = 12),
                        legend.text = element_text( color = '#333333',size = 12),
                        # remove facet 
                        strip.background = element_blank(),
                        strip.text = element_text(size = 0)
                ) +
  
  facet_wrap( ~ hemi)
  
# ggplot2::ggsave(filename = "~/Downloads/lpfc_sa_plot.png",
#                  plot = lpfc_sa_plot,
#                  device = "png",
#                  width = 7,
#                  height = 7,
#                  units = "in",
#                  dpi = "retina")

## normalized
lpfc_sa_normed_plot <- ggplot(group_dev_analysis, aes(x = sulcal_cluster, y = sa_normed)) + 
  
  geom_point(aes(y = sa_normed, fill = age_group), 
              shape = 21, color = 'black', 
              alpha = .5, position = position_jitterdodge()
              ) + 
  
  geom_boxplot(aes(y = sa_normed, fill = age_group),color = 'black',
               outlier.size = 0, outlier.alpha = 0,
               alpha = .6, position = position_dodge(width = 0.75),
               width = 0.5, size = .75) +
  
  scale_fill_manual(breaks = c("children", "adolescent", "young adult"),
                    values = c("#009E73", "#56B4E9", "#E69F00")
                    ) +
  
  labs(x = "cluster group",
       y = "surface area (mm2)") + 
  
  guides(fill = "none", color = "none", alpha = "none") +
  
  scale_y_continuous(n.breaks = 10) +
  
  theme_classic() +
  
  theme( 
                        # set axis title
                        axis.title.x = element_text(color="#333333",
                                                    size=12), 
                        axis.title.y = element_text(color="#333333", 
                                                    angle=90,size=14),
                        # set axis text
                        axis.text = element_text( color='#333333',
                                                 size = 12),
                        # set pannel
                        
                        #panel.border = element_rect(colour = "black", 
                        #                fill=NA, size=1),
                        # set legend
                        legend.title = element_text(color="#333333",size = 12),
                        legend.text = element_text( color = '#333333',size = 12),
                        # remove facet 
                        strip.background = element_blank(),
                        strip.text = element_text(size = 0)
                ) +
  
  facet_wrap( ~ hemi)
  
# ggplot2::ggsave(filename = "~/Downloads/lpfc_sa_normed_plot.png",
#                  plot = lpfc_sa_normed_plot,
#                  device = "png",
#                  width = 7,
#                  height = 7,
#                  units = "in",
#                  dpi = "retina")


# thickness
## raw
lpfc_ct_plot <- ggplot(group_dev_analysis, aes(x = sulcal_cluster, y = cortical_thickness_mean)) + 
  
  geom_point(aes(y = cortical_thickness_mean, fill = age_group), 
              shape = 21, color = 'black', 
              alpha = .5, position = position_jitterdodge()
              ) + 
  
  geom_boxplot(aes(y = cortical_thickness_mean, fill = age_group),color = 'black',
               outlier.size = 0, outlier.alpha = 0,
               alpha = .6, position = position_dodge(width = 0.75),
               width = 0.5, size = .75) +
  
  scale_fill_manual(breaks = c("children", "adolescent", "young adult"),
                    values = c("#009E73", "#56B4E9", "#E69F00")
                    ) +
  
  labs(x = "cluster group",
       y = "cortical thickness (mm)") + 
  
  guides(fill = "none", color = "none", alpha = "none") +
  
  scale_y_continuous(n.breaks = 10) +
  
  theme_classic() +
  
  theme( 
                        # set axis title
                        axis.title.x = element_text(color="#333333",
                                                    size=12), 
                        axis.title.y = element_text(color="#333333", 
                                                    angle=90,size=14),
                        # set axis text
                        axis.text = element_text( color='#333333',
                                                 size = 12),
                        # set pannel
                        
                        #panel.border = element_rect(colour = "black", 
                        #                fill=NA, size=1),
                        # set legend
                        legend.title = element_text(color="#333333",size = 12),
                        legend.text = element_text( color = '#333333',size = 12),
                        # remove facet 
                        strip.background = element_blank(),
                        strip.text = element_text(size = 0)
                ) +
  
  facet_wrap( ~ hemi)
  
# ggplot2::ggsave(filename = "~/Downloads/lpfc_ct_plot.png",
#                  plot = lpfc_ct_plot,
#                  device = "png",
#                  width = 7,
#                  height = 7,
#                  units = "in",
#                  dpi = "retina")

# normalized
lpfc_ct_norm_plot <- ggplot(group_dev_analysis, aes(x = sulcal_cluster, y = cortical_thickness_normed)) + 
  
  geom_point(aes(y = cortical_thickness_normed, fill = age_group), 
              shape = 21, color = 'black', 
              alpha = .5, position = position_jitterdodge()
              ) + 
  
  geom_boxplot(aes(y = cortical_thickness_normed, fill = age_group),color = 'black',
               outlier.size = 0, outlier.alpha = 0,
               alpha = .6, position = position_dodge(width = 0.75),
               width = 0.5, size = .75) +
  
  scale_fill_manual(breaks = c("children", "adolescent", "young adult"),
                    values = c("#009E73", "#56B4E9", "#E69F00")
                    ) +
  
  labs(x = "cluster group",
       y = "cortical thickness (mm)") + 
  
  guides(fill = "none", color = "none", alpha = "none") +
  
  scale_y_continuous(n.breaks = 10) +
  
  theme_classic() +
  
  theme( 
                        # set axis title
                        axis.title.x = element_text(color="#333333",
                                                    size=12), 
                        axis.title.y = element_text(color="#333333", 
                                                    angle=90,size=14),
                        # set axis text
                        axis.text = element_text( color='#333333',
                                                 size = 12),
                        # set pannel
                        
                        #panel.border = element_rect(colour = "black", 
                        #                fill=NA, size=1),
                        # set legend
                        legend.title = element_text(color="#333333",size = 12),
                        legend.text = element_text( color = '#333333',size = 12),
                        # remove facet 
                        strip.background = element_blank(),
                        strip.text = element_text(size = 0)
                ) +
  
  facet_wrap( ~ hemi)
  
#ggplot2::ggsave(filename = "~/Downloads/lpfc_ct_norm_plot.png",
                 # plot = lpfc_ct_norm_plot,
                 # device = "png",
                 # width = 7,
                 # height = 7,
                 # units = "in",
                 # dpi = "retina")
```


##### Continous analysis on morphology
* linear mixed models to test whether depth, surface area, and cortical thickness (raw and normed) changed with age (rather than as a categorical variable) for the children and adolescent sample

* Predictors
* Age
* hemi: lh, rh

###### linear mixed effects models
```{r}
# border sulci
## set up data
group_dev_analysis_border.nora <- group_dev_analysis %>% subset(sulcal_cluster == "border" & age_group %in% c("children", "adolescent"))
group_dev_analysis_border_depth.nora2 <- group_dev_analysis_border.nora %>% group_by(sub, hemi, sulcal_cluster, age) %>% 
                                                                            summarise(mean_depth = mean(sulcal_depth_mm),
                                                                                      mean_thickness = mean(cortical_thickness_mean),
                                                                                      mean_sa = mean(total_surface_area_.mm.2.),
                                                                                      mean_lgi = mean(localGI),
                                                                                      mean_depth_norm = mean(depth_pct_max),
                                                                                      mean_thickness_norm = mean(cortical_thickness_normed),
                                                                                      mean_sa_norm = mean(sa_normed))

## depth
### raw
model_dev_depth <- lme(mean_depth ~ age*hemi, random = (~1|sub/hemi), data = group_dev_analysis_border_depth.nora2)
border_depth_raw <- summary(model_dev_depth)
border_depth_raw_table <- border_depth_raw$tTable
border_depth_raw_table <- as.data.frame(border_depth_raw_table)
border_depth_raw_table$metric <- "depth"
border_depth_raw_table$type <- "raw"

### normalized
model_dev_depth_norm <- lme(mean_depth_norm ~ age*hemi, random = (~1|sub/hemi), data = group_dev_analysis_border_depth.nora2)
border_depth_norm <- summary(model_dev_depth_norm)
border_depth_norm_table <- border_depth_norm$tTable
border_depth_norm_table <- as.data.frame(border_depth_norm_table)
border_depth_norm_table$metric <- "depth"
border_depth_norm_table$type <- "norm"

### combine results
border_depth <- rbind(border_depth_raw_table, border_depth_norm_table)


## thickness
### raw
model_dev_thick <- lme(mean_thickness ~ age*hemi, random = (~1|sub/hemi), data = group_dev_analysis_border_depth.nora2)
border_thick_raw <- summary(model_dev_thick)
border_thick_raw_table <- border_thick_raw$tTable
border_thick_raw_table <- as.data.frame(border_thick_raw_table)
border_thick_raw_table$metric <- "thickness"
border_thick_raw_table$type <- "raw"

### normalized
model_dev_thick_norm <- lme(mean_thickness_norm ~ age*hemi, random = (~1|sub/hemi), data = group_dev_analysis_border_depth.nora2)
border_thick_norm <- summary(model_dev_thick_norm)
border_thick_norm_table <- border_thick_norm$tTable
border_thick_norm_table <- as.data.frame(border_thick_norm_table)
border_thick_norm_table$metric <- "thickness"
border_thick_norm_table$type <- "norm"

### combine results
border_thick <- rbind(border_thick_raw_table, border_thick_norm_table)


## surface area
### raw
model_dev_sa <- lme(mean_sa ~ age*hemi, random = (~1|sub/hemi), data = group_dev_analysis_border_depth.nora2)
border_sa_raw <- summary(model_dev_sa)
border_sa_raw_table <- border_sa_raw$tTable
border_sa_raw_table <- as.data.frame(border_sa_raw_table)
border_sa_raw_table$metric <- "surf"
border_sa_raw_table$type <- "raw"

### normalized
model_dev_sa_norm <- lme(mean_sa_norm ~ age*hemi, random = (~1|sub/hemi), data = group_dev_analysis_border_depth.nora2)
border_sa_norm <- summary(model_dev_sa_norm)
border_sa_norm_table <- border_sa_norm$tTable
border_sa_norm_table <- as.data.frame(border_sa_norm_table)
border_sa_norm_table$metric <- "surf"
border_sa_norm_table$type <- "norm"

### combine results
border_surf <- rbind(border_sa_raw_table, border_sa_norm_table)

### combine all results
border_lme_results <- rbind(border_depth, border_thick, border_surf)
border_lme_results$cluster <- "border"


# dorsal sulci
## set up
group_dev_analysis_dorsal.nora <- group_dev_analysis %>% subset(sulcal_cluster == "dorsal" & age_group %in% c("children", "adolescent"))
group_dev_analysis_dorsal.nora2 <- group_dev_analysis_dorsal.nora %>% group_by(sub, hemi, sulcal_cluster, age) %>% 
                                                                            summarise(mean_depth = mean(sulcal_depth_mm),
                                                                                      mean_thickness = mean(cortical_thickness_mean),
                                                                                      mean_sa = mean(total_surface_area_.mm.2.),
                                                                                      mean_lgi = mean(localGI),
                                                                                      mean_depth_norm = mean(depth_pct_max),
                                                                                      mean_thickness_norm = mean(cortical_thickness_normed),
                                                                                      mean_sa_norm = mean(sa_normed))

## depth
### raw
model_dev_depth2 <- lme(mean_depth ~ age*hemi, random = (~1|sub/hemi), data = group_dev_analysis_dorsal.nora2)
dorsal_depth_raw <- summary(model_dev_depth2)
dorsal_depth_raw_table <- dorsal_depth_raw$tTable
dorsal_depth_raw_table <- as.data.frame(dorsal_depth_raw_table)
dorsal_depth_raw_table$metric <- "depth"
dorsal_depth_raw_table$type <- "raw"

### normalized
model_dev_depth_norm2 <- lme(mean_depth_norm ~ age*hemi, random = (~1|sub/hemi), data = group_dev_analysis_dorsal.nora2)
dorsal_depth_norm <- summary(model_dev_depth_norm2)
dorsal_depth_norm_table <- dorsal_depth_norm$tTable
dorsal_depth_norm_table <- as.data.frame(dorsal_depth_norm_table)
dorsal_depth_norm_table$metric <- "depth"
dorsal_depth_norm_table$type <- "norm"

### combine results
dorsal_depth <- rbind(dorsal_depth_raw_table, dorsal_depth_norm_table)


## thickness
### raw
model_dev_thick2 <- lme(mean_thickness ~ age*hemi, random = (~1|sub/hemi), data = group_dev_analysis_dorsal.nora2)
dorsal_thick_raw <- summary(model_dev_thick2)
dorsal_thick_raw_table <- dorsal_thick_raw$tTable
dorsal_thick_raw_table <- as.data.frame(dorsal_thick_raw_table)
dorsal_thick_raw_table$metric <- "thick"
dorsal_thick_raw_table$type <- "raw"

### normalized
model_dev_thick_norm2 <- lme(mean_thickness_norm ~ age*hemi, random = (~1|sub/hemi), data = group_dev_analysis_dorsal.nora2)
dorsal_thick_norm <- summary(model_dev_thick_norm2)
dorsal_thick_norm_table <- dorsal_thick_norm$tTable
dorsal_thick_norm_table <- as.data.frame(dorsal_thick_norm_table)
dorsal_thick_norm_table$metric <- "thick"
dorsal_thick_norm_table$type <- "norm"

### combine results
dorsal_thick <- rbind(dorsal_thick_raw_table, dorsal_thick_norm_table)


## surface area
### raw
model_dev_sa2 <- lme(mean_sa ~ age*hemi, random = (~1|sub/hemi), data = group_dev_analysis_dorsal.nora2)
dorsal_sa_raw <- summary(model_dev_sa2)
dorsal_sa_raw_table <- dorsal_sa_raw$tTable
dorsal_sa_raw_table <- as.data.frame(dorsal_sa_raw_table)
dorsal_sa_raw_table$metric <- "surf"
dorsal_sa_raw_table$type <- "raw"

### normalized
model_dev_sa_norm2 <- lme(mean_sa_norm ~ age*hemi, random = (~1|sub/hemi), data = group_dev_analysis_dorsal.nora2)
dorsal_sa_norm <- summary(model_dev_sa_norm2)
dorsal_sa_norm_table <- dorsal_sa_norm$tTable
dorsal_sa_norm_table <- as.data.frame(dorsal_sa_norm_table)
dorsal_sa_norm_table$metric <- "surf"
dorsal_sa_norm_table$type <- "norm"

### combine results
dorsal_surf <- rbind(dorsal_sa_raw_table, dorsal_sa_norm_table)

### combine all results
dorsal_lme_results <- rbind(dorsal_depth, dorsal_thick, dorsal_surf)
dorsal_lme_results$cluster <- "dorsal"



# ventral sulci
## set up
group_dev_analysis_ventral.nora <- group_dev_analysis %>% subset(sulcal_cluster == "ventral" & age_group %in% c("children", "adolescent"))
group_dev_analysis_ventral.nora2 <- group_dev_analysis_ventral.nora %>% group_by(sub, hemi, sulcal_cluster, age) %>% 
                                                                            summarise(mean_depth = mean(sulcal_depth_mm),
                                                                                      mean_thickness = mean(cortical_thickness_mean),
                                                                                      mean_sa = mean(total_surface_area_.mm.2.),
                                                                                      mean_lgi = mean(localGI),
                                                                                      mean_depth_norm = mean(depth_pct_max),
                                                                                      mean_thickness_norm = mean(cortical_thickness_normed),
                                                                                      mean_sa_norm = mean(sa_normed))

## depth
### raw
model_dev_depth3 <- lme(mean_depth ~ age*hemi, random = (~1|sub/hemi), data = group_dev_analysis_ventral.nora2)
ventral_depth_raw <- summary(model_dev_depth3)
ventral_depth_raw_table <- ventral_depth_raw$tTable
ventral_depth_raw_table <- as.data.frame(ventral_depth_raw_table)
ventral_depth_raw_table$metric <- "depth"
ventral_depth_raw_table$type <- "raw"

### normalized
model_dev_depth_norm3 <- lme(mean_depth_norm ~ age*hemi, random = (~1|sub/hemi), data = group_dev_analysis_ventral.nora2)
ventral_depth_norm <- summary(model_dev_depth_norm3)
ventral_depth_norm_table <- ventral_depth_norm$tTable
ventral_depth_norm_table <- as.data.frame(ventral_depth_norm_table)
ventral_depth_norm_table$metric <- "depth"
ventral_depth_norm_table$type <- "norm"

### combine results
ventral_depth <- rbind(ventral_depth_raw_table, ventral_depth_norm_table)


## thickness
### raw
model_dev_thick3 <- lme(mean_thickness ~ age*hemi, random = (~1|sub/hemi), data = group_dev_analysis_ventral.nora2)
ventral_thick_raw <- summary(model_dev_thick3)
ventral_thick_raw_table <- ventral_thick_raw$tTable
ventral_thick_raw_table <- as.data.frame(ventral_thick_raw_table)
ventral_thick_raw_table$metric <- "thick"
ventral_thick_raw_table$type <- "raw"

### normalized
model_dev_thick_norm3 <- lme(mean_thickness_norm ~ age*hemi, random = (~1|sub/hemi), data = group_dev_analysis_ventral.nora2)
ventral_thick_norm <- summary(model_dev_thick_norm3)
ventral_thick_norm_table <- ventral_thick_norm$tTable
ventral_thick_norm_table <- as.data.frame(ventral_thick_norm_table)
ventral_thick_norm_table$metric <- "thick"
ventral_thick_norm_table$type <- "norm"

### combine results
ventral_thick <- rbind(ventral_thick_raw_table, ventral_thick_norm_table)


## surface area
### raw
model_dev_sa3 <- lme(mean_sa ~ age*hemi, random = (~1|sub/hemi), data = group_dev_analysis_ventral.nora2)
ventral_sa_raw <- summary(model_dev_sa3)
ventral_sa_raw_table <- ventral_sa_raw$tTable
ventral_sa_raw_table <- as.data.frame(ventral_sa_raw_table)
ventral_sa_raw_table$metric <- "surf"
ventral_sa_raw_table$type <- "raw"

### normalized
model_dev_sa_norm3 <- lme(mean_sa_norm ~ age*hemi, random = (~1|sub/hemi), data = group_dev_analysis_ventral.nora2)
ventral_sa_norm <- summary(model_dev_sa_norm3)
ventral_sa_norm_table <- ventral_sa_norm$tTable
ventral_sa_norm_table <- as.data.frame(ventral_sa_norm_table)
ventral_sa_norm_table$metric <- "surf"
ventral_sa_norm_table$type <- "norm"

### combine results
ventral_surf <- rbind(ventral_sa_raw_table, ventral_sa_norm_table)

### combine all results
ventral_lme_results <- rbind(ventral_depth, ventral_thick, ventral_surf)
ventral_lme_results$cluster <- "ventral"


# combine all results for all sulcal groups
age_lme_results <- rbind(border_lme_results, dorsal_lme_results, ventral_lme_results) 

## conduct FDR correction
p_val_tst_adj_lme <- p.adjust(p = age_lme_results$`p-value`, 
                              method = "fdr")

## round values to be more readable
p_val_tst_adj <- round(as.data.frame(p_val_tst_adj), 3) # round

## adjustments to table
### merge adjusted with original
age_lme_results <- cbind(age_lme_results, p_val_tst_adj_lme)

age_lme_results <- age_lme_results %>% mutate(signif = case_when(p_val_tst_adj_lme >= .1 ~ "", 
                                  p_val_tst_adj_lme < .1 & p_val_tst_adj_lme >= .05 ~ "+",
                                  p_val_tst_adj_lme < .05 & p_val_tst_adj_lme >= .01 ~ "*",
                                  p_val_tst_adj_lme < .01 & p_val_tst_adj_lme >= .001 ~ "**",
                                  p_val_tst_adj_lme < .001 ~ "***" 
                             ))

```

#### Figure 4D and 4-1D: Visualizing lme results
```{r}
# import table made in previous cell
cross_sectional_correlations <- read.csv("./data/morphological_analysis/crosssectional_data/cross_sectional_continuous.csv")

# theme
theme_cs_cor <- theme( 
                        # set axis title
                        axis.title.x = element_text(color="#333333",
                                                    size=12), 
                        axis.title.y = element_text(color="#333333", 
                                                    angle=90, 
                                                    size=14
                                                    ),
                        # rotate x-axis text
                        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),

                        # set axis text
                        axis.text = element_text(color='#333333',
                                                 size = 12),
                        # set pannel
                        
                        #panel.border = element_rect(colour = "black", 
                        #                fill=NA, size=1),
                        # set legend
                        legend.title = element_text(color="#333333",size = 12),
                        legend.text = element_text( color = '#333333',size = 12),
                        # remove facet 
                        strip.background = element_blank()#,
                        #strip.text = element_text(size = 0)
                ) 

# raw plots
cross_sectional_correlations.raw.plot <- cross_sectional_correlations %>% 
  
  subset(type == "raw" & metric %in% c("depth", "thickness")) %>%
  
  ggplot(aes(x = cluster, y = beta)) + 
  
  geom_col(aes(fill = p.value), color = "black") +
  
  scale_fill_continuous(limits = c(0.000001, 0.1)) +
  
  labs(x = "cluster",
       y = "age beta-value") + 
  
  facet_wrap( ~ metric) +
  
  scale_y_continuous(n.breaks = 10) +
  
  theme_classic() + 
  
  theme( 
                        # set axis title
                        axis.title.x = element_text(color="#333333",
                                                    size=12), 
                        axis.title.y = element_text(color="#333333", 
                                                    angle=90,size=14),
                        # set axis text
                        axis.text = element_text( color='#333333',
                                                 size = 12),
                        # set pannel
                        
                        #panel.border = element_rect(colour = "black", 
                        #                fill=NA, size=1),
                        # set legend
                        legend.title = element_text(color="#333333",size = 12),
                        legend.text = element_text( color = '#333333',size = 12),
                        # remove facet 
                        strip.background = element_blank(),
                        strip.text = element_text(size = 0)
                )
  
cross_sectional_correlations.raw.plot
  
# ggplot2::ggsave(filename = "~/Desktop/cross_sectional_correlations_raw_plot.png",
#                  plot = cross_sectional_correlations.raw.plot,
#                  device = "png",
#                  width = 6,
#                  height = 7,
#                  units = "in",
#                  dpi = "retina")

cross_sectional_correlations.sa.plot <- cross_sectional_correlations %>% 
  
  subset(type == "raw" & metric %in% c("surface_area")) %>%
  
  ggplot(aes(x = cluster, y = beta)) + 
  
  geom_col(aes(fill = p.value), color = "black") +
  
  scale_fill_continuous(limits = c(0.000001, 0.1)) +

  labs(x = "raw metric",
       y = "age beta-value") + 

  facet_wrap( ~ metric) +
  
  scale_y_continuous(n.breaks = 10) +
  
  theme_classic() + 
  
  theme( 
                        # set axis title
                        axis.title.x = element_text(color="#333333",
                                                    size=12), 
                        axis.title.y = element_text(color="#333333", 
                                                    angle=90,size=14),
                        # set axis text
                        axis.text = element_text( color='#333333',
                                                 size = 12),
                        # set pannel
                        
                        #panel.border = element_rect(colour = "black", 
                        #                fill=NA, size=1),
                        # set legend
                        legend.title = element_text(color="#333333",size = 12),
                        legend.text = element_text( color = '#333333',size = 12),
                        # remove facet 
                        strip.background = element_blank(),
                        strip.text = element_text(size = 0)
                ) +
  
  guides(fill = "none")
  
  
# ggplot2::ggsave(filename = "~/Desktop/cross_sectional_correlations_raw_sa_plot.png",
#                  plot = cross_sectional_correlations.sa.plot,
#                  device = "png",
#                  width = 3,
#                  height = 7,
#                  units = "in",
#                  dpi = "retina")


# normalized plots
cross_sectional_correlations.norm.plot <- cross_sectional_correlations %>% 
  
  subset(type == "norm" & metric %in% c("depth", "thickness")) %>%
  
  ggplot(aes(x = cluster, y = beta)) +
  
  geom_col(aes(fill = p.value), color = "black") +
  
  scale_fill_continuous(limits = c(0.000001, 0.1)) +

  labs(x = "normed metric",
       y = "age beta-value") + 
  
  facet_wrap( ~ metric) +
  
  scale_y_continuous(n.breaks = 10) +
  
  theme_classic() + 
  
  theme( 
                        # set axis title
                        axis.title.x = element_text(color="#333333",
                                                    size=12), 
                        axis.title.y = element_text(color="#333333", 
                                                    angle=90,size=14),
                        # set axis text
                        axis.text = element_text( color='#333333',
                                                 size = 12),
                        # set pannel
                        
                        #panel.border = element_rect(colour = "black", 
                        #                fill=NA, size=1),
                        # set legend
                        legend.title = element_text(color="#333333",size = 12),
                        legend.text = element_text( color = '#333333',size = 12),
                        # remove facet 
                        strip.background = element_blank(),
                        strip.text = element_text(size = 0)
                )
  
cross_sectional_correlations.norm.plot
  
# ggplot2::ggsave(filename = "~/Desktop/cross_sectional_correlations_norm_plot.png",
#                  plot = cross_sectional_correlations.norm.plot,
#                  device = "png",
#                  width = 6,
#                  height = 7,
#                  units = "in",
#                  dpi = "retina")

cross_sectional_correlations.sa_norm.plot <- cross_sectional_correlations %>% 
  
  subset(type == "norm" & metric %in% c("surface_area")) %>%
  
  ggplot(aes(x = cluster, y = beta*10^6)) + 
  
  geom_col(aes(fill = p.value), color = "black") +
  
  scale_fill_continuous(limits = c(0.000001, 0.1)) +

  labs(x = "normed metric",
       y = "age beta-value ( x 10^6)") + 
  
  facet_wrap( ~ metric) +
  
  scale_y_continuous(n.breaks = 10) +
  
  theme_classic() + 
  
  theme( 
                        # set axis title
                        axis.title.x = element_text(color="#333333",
                                                    size=12), 
                        axis.title.y = element_text(color="#333333", 
                                                    angle=90,size=14),
                        # set axis text
                        axis.text = element_text( color='#333333',
                                                 size = 12),
                        # set pannel
                        
                        #panel.border = element_rect(colour = "black", 
                        #                fill=NA, size=1),
                        # set legend
                        legend.title = element_text(color="#333333",size = 12),
                        legend.text = element_text( color = '#333333',size = 12),
                        # remove facet 
                        strip.background = element_blank(),
                        strip.text = element_text(size = 0)
                ) +
  
  guides(fill = "none")

cross_sectional_correlations.sa_norm.plot
  
# ggplot2::ggsave(filename = "~/Desktop/cross_sectional_correlations_norm_sa_plot.png",
#                  plot = cross_sectional_correlations.sa_norm.plot,
#                  device = "png",
#                  width = 3,
#                  height = 7,
#                  units = "in",
#                  dpi = "retina")
```


#### Morphological analysis: Longitudinal analyses between two timepoints

##### Data
```{r}
data <- read.csv("./data/morphological_analysis/longitudinal_data/cluster_morphology_longitudinal.csv")

# center age to minimum age
data$age1s <- data$age1 - 6.25
  
# make dataframe for each sulcal cluster in each hemisphere
data.border <- data %>% subset(clusters == "border")
data.border.lh <- data.border %>% subset(hemi == "lh")
data.border.rh <- data.border %>% subset(hemi == "rh")

data.dorsal <-  data %>% subset(clusters == "dlpfc")
data.dorsal.lh <- data.dorsal %>% subset(hemi == "lh")
data.dorsal.rh <- data.dorsal %>% subset(hemi == "rh")

data.ventral <-  data %>% subset(clusters == "vlpfc")
data.ventral.lh <- data.ventral %>% subset(hemi == "lh")
data.ventral.rh <- data.ventral %>% subset(hemi == "rh")
```

##### Stats
* Linear growth curve model (LGC) to test for longitduinal changes in depth and cortical thickness
* One LGC for each cluster in each hemisphere 
* Clusters: Border, Dorsal, & Ventral
* Hemispheres: left = LH & right = RH

###### Border LH thickness
```{r}
myModel.border = '
	#level and slope
	ly0 =~ 1*cort1
	ly0 =~ 1*cort2

	lys =~ 0*cort1
	lys =~ 1*cort2

	# means
	ly0 ~ 1
	lys ~ 1
	cort1 ~ 0
	cort2 ~ 0
	
	# variances
	cort1 ~~ ve*cort1
	cort2 ~~ ve*cort2
	ly0 ~~ ly0
	lys ~~ lys
  # constraining model setting covariance to 0 --> change ve* to estimate after and remove 0* below
	ly0 ~~ 0*lys
	
	# regressions
  #ly0 ~ age1s
  #lys ~ age1s
'

fit.covariate.border.lh <- sem(myModel.border, data = data.border.lh, fixed.x = F)
fit.border.lh <- summary(fit.covariate.border.lh, fit.measures = T, standardized = F)
fit.border.lh
```

###### Border RH thickness
```{r}
fit.covariate.border.rh <- sem(myModel.border, data = data.border.rh, fixed.x = F)
fit.border.rh <- summary(fit.covariate.border.rh, fit.measures = T, standardized = F)
fit.border.rh
```

###### Dorsal LH thickness
```{r}
myModel.dorsal = '
	#level and slope
	ly0 =~ 1*cort1
	ly0 =~ 1*cort2

	lys =~ 0*cort1
	lys =~ 1*cort2

	# means
	ly0 ~ 1
	lys ~ 1
	cort1 ~ 0
	cort2 ~ 0
	
	# variances
	cort1 ~~ ve*cort1
	cort2 ~~ ve*cort2
	ly0 ~~ ly0
	lys ~~ lys
  # constraining model setting covariance to 0 --> change ve* to estimate after and remove 0* below
	ly0 ~~ 0*lys
	
	# regressions
	#ly0 ~ age1s
	#lys ~ age1s
	'

fit.covariate.dorsal.lh <- sem(myModel.dorsal, data = data.dorsal.lh, fixed.x = F)
fit.dorsal.lh <- summary(fit.covariate.dorsal.lh, fit.measures = T, standardized = F)
fit.dorsal.lh
```

###### Dorsal RH thickness
```{r}
fit.covariate.dorsal.rh <- sem(myModel.dorsal, data = data.dorsal.rh, fixed.x = F)
fit.dorsal.rh <- summary(fit.covariate.dorsal.rh, fit.measures = T, standardized = F)
fit.dorsal.rh
```

###### Ventral LH thickness
```{r}
myModel.ventral = '
	#level and slope
	ly0 =~ 1*cort1
	ly0 =~ 1*cort2

	lys =~ 0*cort1
	lys =~ 1*cort2

	# means
	ly0 ~ 1
	lys ~ 1
	cort1 ~ 0
	cort2 ~ 0
	
	# variances
	cort1 ~~ ve*cort1
	cort2 ~~ ve*cort2
	ly0 ~~ ly0
	lys ~~ lys
  # constraining model setting covariance to 0 --> change ve* to estimate after and remove 0* below
	ly0 ~~ 0*lys
	
	# regressions
	#ly0 ~ age1s
	#lys ~ age1s
	'

fit.covariate.ventral.lh = sem(myModel.ventral, data = data.ventral.lh, fixed.x = F)
fit.ventral.lh <- summary(fit.covariate.ventral.lh, fit.measures=T, standardized = F)
fit.ventral.lh
```

###### Ventral RH thickness
```{r}
fit.covariate.ventral.rh <- sem(myModel.ventral, data = data.ventral.rh, fixed.x = F)
fit.ventral.rh <- summary(fit.covariate.ventral.rh, fit.measures = T, standardized = F)
fit.ventral.rh
```

###### Border LH depth
```{r}
myModel.border.depth = '
	#level and slope
	ly0 =~ 1*depth1
	ly0 =~ 1*depth2

	lys =~ 0*depth1
	lys =~ 1*depth2

	# means
	ly0 ~ 1
	lys ~ 1
	depth1 ~ 0
	depth2 ~ 0
	
	# variances
	depth1 ~~ ve*depth1
	depth2 ~~ ve*depth2
	ly0 ~~ ly0
	lys ~~ lys
  # constraining model setting covariance to 0 --> change ve* to estimate after and remove 0* below
	ly0 ~~ 0*lys
	
	# regressions
	#ly0 ~ age1s
	#lys ~ age1s
	'

fit.covariate.border.depth.lh <- sem(myModel.border.depth, data = data.border.lh, fixed.x = F)
fit.border.depth.lh <- summary(fit.covariate.border.depth.lh, fit.measures = T, standardized = F)
fit.border.depth.lh
```

###### Border RH depth
```{r}
fit.covariate.border.depth.rh <- sem(myModel.border.depth, data = data.border.rh, fixed.x = F)
fit.border.depth.rh <- summary(fit.covariate.border.depth.rh, fit.measures = T, standardized = F)
fit.border.depth.lh
```

###### Dorsal LH depth
```{r}
myModel.dorsal.depth = '
	#level and slope
	ly0 =~ 1*depth1
	ly0 =~ 1*depth2

	lys =~ 0*depth1
	lys =~ 1*depth2

	# means
	ly0 ~ 1
	lys ~ 1
	depth1 ~ 0
	depth2 ~ 0
	
	# variances
	depth1 ~~ ve*depth1
	depth2 ~~ ve*depth2
	ly0 ~~ ly0
	lys ~~ lys
  # constraining model setting covariance to 0 --> change ve* to estimate after and remove 0* below
	ly0 ~~ 0*lys
	
	# regressions
  #ly0 ~ age1s
	#lys ~ age1s
	'

fit.covariate.depth.dorsal.lh <- sem(myModel.dorsal.depth, data = data.dorsal.lh, fixed.x = F)
fit.dorsal.depth.lh <- summary(fit.covariate.depth.dorsal.lh, fit.measures = T, standardized = F)
fit.dorsal.depth.lh
```

###### Dorsal RH depth
```{r}
fit.covariate.depth.dorsal.rh <- sem(myModel.dorsal.depth, data = data.dorsal.rh, fixed.x = F)
fit.dorsal.depth.rh <- summary(fit.covariate.depth.dorsal.rh, fit.measures = T, standardized = F)
fit.dorsal.depth.rh
```

###### Ventral LH depth
```{r}
myModel.ventral.depth = '
	#level and slope
	ly0 =~ 1*depth1
	ly0 =~ 1*depth2

	lys =~ 0*depth1
	lys =~ 1*depth2

	# means
	ly0 ~ 1
	lys ~ 1
	depth1 ~ 0
	depth2 ~ 0
	
	# variances
	depth1 ~~ ve*depth1
	depth2 ~~ ve*depth2
	ly0 ~~ ly0
	lys ~~ lys
  # constraining model setting covariance to 0 --> change ve* to estimate after and remove 0* below
	ly0 ~~ 0*lys
	
	# regressions
  #ly0 ~ age1s
	#lys ~ age1s
	'

fit.covariate.depth.ventral.lh <- sem(myModel.ventral.depth, data = data.vlpfc.lh, fixed.x = F)
fit.ventral.depth.lh <- summary(fit.covariate.depth.ventral.lh, fit.measures = T, standardized = F)
fit.ventral.depth.lh
```

###### Ventral RH depth
```{r}
fit.covariate.depth.ventral.rh = sem(myModel.ventral.depth, data = data.ventral.rh, fixed.x = F)
fit.ventral.depth.rh <- summary(fit.covariate.depth.ventral.rh, fit.measures = T, standardized = F)
fit.ventral.depth.rh
```

###### Visualization for longitudinal results 
```{r}
data$clusters <- gsub("dlpfc", "dorsal", data$clusters)
data$clusters <- gsub("vlpfc", "ventral", data$clusters)

data.thick <- data %>% select(c("case", "id", "hemi", "clusters", "cort1", "cort2", "age1", "age2"))
data.thick.t1 <- data.thick %>% select(c("case", "id", "hemi", "clusters", "cort1", "age1")) %>% rename(thickness = cort1,
                                                                                                        age = age1)
data.thick.t2 <- data.thick %>% select(c("case", "id", "hemi", "clusters", "cort2", "age2")) %>% rename(thickness = cort2,
                                                                                                age = age2)
data.thick.l <- rbind(data.thick.t1, data.thick.t2)


### 
set.seed(1)
color = grDevices::colors()[grep('gr(a|e)y', grDevices::colors(), invert = T)]
col_long_subs=sample(color, 44)
col_long_subs

data.thick.l$id <- as.factor(data.thick.l$id)

thick.lh <- data.thick.l %>% subset(hemi == "lh") %>% 
  ggplot(aes(x = age, y = thickness)) + 
  geom_line(aes(group = id)) +
  geom_point(size = 2, shape = 21, aes(fill = id)) + 
 # geom_smooth(aes(color=clusters)) + 
  labs(x = "Age",
       y = "cortical thickness (mm)") + 
  guides(fill = "none") +
  facet_wrap( ~ clusters, 
              strip.position = "top",
              scales = "free_x") +
  scale_fill_manual(breaks = id, 
                    values = col_long_subs) 

ggplot2::ggsave(filename = "~/Desktop/thick.lh.png",
                 plot = thick.lh,
                 device = "png",
                 width = 6,
                 height = 6, 
                 units = "in",
                 dpi = "retina")

thick.rh <- data.thick.l %>% subset(hemi == "rh") %>% 
  ggplot(aes(x = age, y = thickness)) + 
  geom_line(aes(group = id)) +
  geom_point(size = 2, shape = 21, aes(fill = id)) + 
 # geom_smooth(aes(color=clusters)) + 
  labs(x = "Age",
       y = "cortical thickness (mm)") + 
  guides(fill = "none") +
  facet_wrap( ~ clusters, 
              strip.position = "top",
              scales = "free_x") +
  scale_fill_manual(breaks = id, 
                    values = col_long_subs) 

ggplot2::ggsave(filename = "~/Desktop/thick.rh.png",
                 plot = thick.rh,
                 device = "png",
                 width = 6,
                 height = 6, 
                 units = "in",
                 dpi = "retina")

##

data.depth <- data %>% select(c("case", "id", "hemi", "clusters", "depth1", "depth2", "age1", "age2"))
data.depth.t1 <- data.depth %>% select(c("case", "id", "hemi", "clusters", "depth1", "age1")) %>% rename(depth = depth1,
                                                                                                        age = age1)
data.depth.t2 <- data.depth %>% select(c("case", "id", "hemi", "clusters", "depth2", "age2")) %>% rename(depth = depth2,
                                                                                                age = age2)
data.depth.l <- rbind(data.depth.t1, data.depth.t2)


### 
set.seed(1)
color = grDevices::colors()[grep('gr(a|e)y', grDevices::colors(), invert = T)]
col_long_subs=sample(color, 44)
col_long_subs

data.depth.l$id <- as.factor(data.depth.l$id)

depth.lh <- data.depth.l %>% subset(hemi == "lh") %>% 
  ggplot(aes(x = age, y = depth)) + 
  geom_line(aes(group = id)) +
  geom_point(size = 2, shape = 21, aes(fill = id)) + 
 # geom_smooth(aes(color=clusters)) + 
  labs(x = "Age",
       y = "depth  (mm)") + 
  guides(fill = "none") +
  facet_wrap( ~ clusters, 
              strip.position = "top",
              scales = "free_x") +
  scale_fill_manual(breaks = id, 
                    values = col_long_subs) 

ggplot2::ggsave(filename = "~/Desktop/depth.lh.png",
                 plot = depth.lh,
                 device = "png",
                 width = 6,
                 height = 6, 
                 units = "in",
                 dpi = "retina")

depth.rh <- data.depth.l %>% subset(hemi == "rh") %>% 
  ggplot(aes(x = age, y = depth)) + 
  geom_line(aes(group = id)) +
  geom_point(size = 2, shape = 21, aes(fill = id)) + 
 # geom_smooth(aes(color=clusters)) + 
  labs(x = "Age",
       y = "depth (mm)") + 
  guides(fill = "none") +
  facet_wrap( ~ clusters, 
              strip.position = "top",
              scales = "free_x") +
  scale_fill_manual(breaks = id, 
                    values = col_long_subs) 

ggplot2::ggsave(filename = "~/Desktop/depth.rh.png",
                 plot = depth.rh,
                 device = "png",
                 width = 6,
                 height = 6, 
                 units = "in",
                 dpi = "retina")

```


#### Behavioral analysis: Visualizations for LASSO and LooCV analyses
* See Jupyter Notebook for the actual LASSO and LooCV analyses

##### Data
```{r}
lasso_coefs <- read.csv('./data/morphological_analysis/behavioral_data/lasso_coefs.csv')
lasso_mse <- read.csv("./data/morphological_analysis/behavioral_data/lasso_MSE.csv")
mod1a <- read.csv("./data/morphological_analysis/behavioral_data/mod1a_pred.csv")
```

##### Figure 5: LASSO analysis results
```{r}
# LASSO beta plot
## set up
lasso_coefs$Sulci <- factor(lasso_coefs$Sulci, 
                                         levels = c("central", "iprs", "sprs", 
                                                    "sfs_p", "sfs_a", "imfs_h", "imfs_v",
                                                    "pmfs_p", "pmfs_i", "pmfs_a",
                                                    "ifs", 
                                                    "ds", "ts", "aalf",
                                                    "half", "prts", "lfms"))
lasso_coefs$Sulci <- gsub("central", "cs", lasso_coefs$Sulci)
lasso_coefs$Sulci <- gsub("sfs_p", "sfs-p", lasso_coefs$Sulci)
lasso_coefs$Sulci <- gsub("sfs_a", "sfs-a", lasso_coefs$Sulci)
lasso_coefs$Sulci <- gsub("imfs_h", "imfs-h", lasso_coefs$Sulci)
lasso_coefs$Sulci <- gsub("imfs_v", "imfs-v", lasso_coefs$Sulci)
lasso_coefs$Sulci <- gsub("pmfs_p", "pmfs-p", lasso_coefs$Sulci)
lasso_coefs$Sulci <- gsub("pmfs_i", "pmfs-i", lasso_coefs$Sulci)
lasso_coefs$Sulci <- gsub("pmfs_a", "pmfs-a", lasso_coefs$Sulci)


## make tile plot for lasso coefs
lasso_coef_plt <- ggplot(data = lasso_coefs, aes(x=as.factor(alpha_level), y=as.factor(Sulci))) +
                
                geom_tile(aes(fill = beta), size=0.3) +
                
                coord_equal() +
  
                scale_y_discrete(limits = rev(levels(lasso_coefs$Sulci))) +

                scale_fill_gradient2(low = scales::muted("#f4a582"), mid = "white", high = scales::muted("#92c5de"),
                                    midpoint = 0, space = "Lab", na.value = "grey50",
                                    guide = "colourbar", aesthetics = "fill") +

                
                geom_text(aes(label=round(beta, digits = 2), 
                              size = 2), size = 4) +
                
                xlab("alpha level") +
                ylab('lateral PFC sulci') +
                labs(fill = "abs. beta") +
                
                theme(
                        # set axis title
                        axis.title.x = element_text(color="#333333",
                                                    size=12), 
                        axis.title.y = element_text(color="#333333", 
                                                    angle=90,size=14),
                        # set axis text
                        axis.text = element_text( color='#333333',
                                                 size = 12),
                        # set pannel
                        
                        #panel.border = element_rect(colour = "black", 
                        #                fill=NA, size=1),
                        # set legend
                        legend.title = element_text(color="#333333",size = 12),
                        legend.text = element_text( color = '#333333',size = 12),
                        axis.line = element_blank(),
                        axis.ticks = element_blank(),
                        # set aspect ratio
                        aspect.ratio = 1/1
                )

# ggplot2::ggsave(filename = "~/Desktop/lasso_coef_plt.png",
#                  plot = lasso_coef_plt,
#                  device = "png",
#                  width = 7,
#                  height = 7, 
#                  units = "in",
#                  dpi = "retina")


# make line plot of MSE ###

spline_int <- as.data.frame(spline(log(lasso_mse$alpha), lasso_mse$MSE))
MSE <- ggplot(spline_int, aes(x = x, y = y)) +
  
        geom_line(color = "gray", size = 1) +

        geom_vline(xintercept = log(0.07), 
                   linetype="dotted", 
                   size = 2) +
  
        xlab ('alpha-level')+
        ylab(' Cross Validated MSE') +
        
        theme_classic() +

        theme(
            # set axis title
            axis.title.x = element_text(color="#333333",
                                          size=14), 
            axis.title.y = element_text(color="#333333",
                                        angle=90,size=14),
            # set axis text
            axis.text = element_text( color='#333333', 
                                     size = 12 ,hjust =0),
            # set lengend
            legend.text = element_text( color = '#333333',
                                       size = 12), 
            # set pannel
            panel.grid.minor=element_blank(),
            legend.title = element_text(color="#333333",
                                        size = 12),
            panel.border = element_rect(colour = "black", 
                                        fill=NA, size = 1),
            axis.line = element_blank()
            # set aspect ratio
            #aspect.ratio = 10/20
            ) +
  
  scale_x_continuous(limits = c(log(.012), log(1)))

# ggplot2::ggsave(filename = "~/Desktop/MSE.png",
#                  plot = MSE,
#                  device = "png",
#                  width = 7,
#                  height = 3, 
#                  units = "in",
#                  dpi = "retina")


# MSE bar plot
MSE_cv <- data.frame(
  "model" <- c("Age", "All_Age", "Selected_Age"),
  "MSE" <- c(23.03, 41.69, 19.94))

xticks_labels <- c("Baseline \nAge", "All Sulci + \nBaseline Age", "Selected Sulci + \nBaseline Age")

MSE_CV_plt <- ggplot(MSE_cv, aes(x = model)) +
  
  geom_col(aes(y = MSE, fill = model), color = 'black') +
  
  scale_fill_manual(breaks = c("Age", "All_Age", "Selected_Age"),
                    values = c("#404040", "#bababa", "#ffffff")) +
  
  xlab ('Model') +
  ylab('Mean Squared Error') +
  
  scale_x_discrete(breaks = c("Age", "All_Age", "Selected_Age"),
                   labels = xticks_labels) +
  
  theme(
                        # set axis title
                        axis.title.x = element_text(color="#333333",
                                                    size=12), 
                        axis.title.y = element_text(color="#333333", 
                                                    angle=90,size=14),
                        # set axis text
                        axis.text = element_text( color='#333333',
                                                 size = 12),
                        # set pannel
                        
                        #panel.border = element_rect(colour = "black", 
                        #                fill=NA, size=1),
                        # set legend
                        legend.title = element_text(color="#333333",size = 12),
                        legend.text = element_text( color = '#333333',size = 12)
                        # set aspect ratio
                ) + 
  
  guides(fill = 'none')

# ggplot2::ggsave(filename = "~/Desktop/MSE_CV_plt.png",
#                  plot = MSE_CV_plt,
#                  device = "png",
#                  width = 6,
#                  height = 3, 
#                  units = "in",
#                  dpi = "retina")


# scatter plot to visualize cor test
## whole sample
cor.test(mod1a$Measured, mod1a$predicted, method = "spearman") # r = 0.46, p = .002
  
## plot
scatter_pred_plot <- mod1a.c %>% ggplot(aes(x = Measured, y = predicted)) +
  
    geom_point(shape = 21, 
                size = 2,
                fill = "gray") +
  
    geom_smooth(aes(y = predicted),
                # linear reg line
                method = "lm",
                # incl. standard error
                se = TRUE,
                fill = "gray",
                #line asthetics
                color = "black", 
                alpha = 0.5
               # , linetype="dashed
               ) + 
  
  scale_x_continuous(n.breaks = 6) +
  scale_y_continuous(n.breaks = 6) +
  
  theme_classic() +
  theme(
                        # set axis title
                        axis.title.x = element_text(color="#333333",
                                                    size=12), 
                        axis.title.y = element_text(color="#333333", 
                                                    angle=90,size=14),
                        # set axis text
                        axis.text = element_text( color='#333333',
                                                 size = 12),
                        # set pannel
                        
                        #panel.border = element_rect(colour = "black", 
                        #                fill=NA, size=1),
                        # set legend
                        legend.title = element_text(color="#333333",size = 12),
                        legend.text = element_text( color = '#333333',size = 12)
    )

# ggplot2::ggsave(filename = "~/Desktop/scatter_pred_plot.png",
#                  plot = scatter_pred_plot,
#                  device = "png",
#                  width = 6,
#                  height = 4, 
#                  units = "in",
#                  dpi = "retina")
```


#### Tables 

##### Table 1: Cross-sectional demographics 
```{r}
dev_demographics <- data.frame("Age group" <- c("Children", "Adolescents", "Young Adults"),
                               #"n" <- c(36, 36, 36),
                               "n (%F)" <- c("36 (47.2)", "36 (36.1)", "36 (47.2)"),
                               "Age (years) " <- c("8.9  1.59", "15.21  2.15", "28.97  3.78"),
                               "Age range (years)" <- c("6.41-11.53", "11.66-18.86", "22-36") 
                               )
names(dev_demographics)[1] <- "Age group"
names(dev_demographics)[2] <- "n (%F)"
names(dev_demographics)[3] <- "Age (years)"
names(dev_demographics)[4] <- "Age range (years)"
dev_demographics

dev_demographics.tab <- dev_demographics %>% 
  gt() %>%
  # tab_header(
  #   title = md("**Table 2**"),
  #   subtitle = md("*Gender and age demographics of the three age groups*")) %>%
  #tab_source_note(md("*Note.* The *age* column depicts average age  sd.")) %>%
  # tab_options(table.font.size = 20,
  #             heading.title.font.size = 20,
  #             heading.subtitle.font.size = 20,
  #             heading.align = "left",
  #             heading.border.bottom.color = 'black',
  #             table.border.top.color = "white",
  #             column_labels.border.top.color = "black",
  #             column_labels.border.bottom.color = "black",
  #             column_labels.vlines.color = "black",
  #             row_group.border.bottom.color = "black",
  #             row_group.border.top.color = "black",
  #             row_group.border.right.color = "black",
  #             stub.border.color = "black",
  #             table_body.border.bottom.color = "black",
  #             table_body.hlines.color = "black",
  #             table_body.vlines.color = "black",
  #             table.border.bottom.color = "white",
  #             table.width = pct(100),
  #             table.background.color = "white") %>%
  cols_align(align="left", columns = 1) %>%
  cols_align(align="center", columns = 2:4) %>%
  
  tab_style(
    style = list(
      cell_borders(
        sides = c("top", "bottom"),
        color = "white",
        weight = px(1)
      ),
      #cell_text(
      #  align="center"
      #),
      cell_fill(color = "white", alpha = NULL)
    ),
    locations = cells_body(
      columns = everything(),
      rows = everything()
    )
  ) %>%
  opt_table_font(font = google_font(name = "Times"))

# gtsave(dev_demographics.tab, file = "~/Desktop/DropBox/DEVPFC_morphology/ms/Fig_tiff/Table_1.rtf"
# )
```

##### Extended Data Tables 1-1 and 1-2: Additional cross-sectional demographics 
```{r}
ca_demographics <- data.frame(
  "16,000-24,999" <- c(2),
  "25,000-34,999" <- c(3),
  "50,000-74,999" <- c(6), 
  "75,000-99,999" <- c(8), 
  "100,000-199,999" <- c(27),
  "Over 200,000" <- c(5),
  "Unknown/Not Reported" <- c(21), 
  
  "High School/GED" <- c(8),
  "Vocational" <- c(1),
  "Associate degree" <- c(6),
  "Bachelor's degree" <- c(18), 
  "Master's degree" <- c(15),
  "Doctorate" <- c(4),
  "Professional" <- c(3),
  "Other" <- c(3),
  "None of the above (less than high school)" <- c(1),
  "Unknown/Not Reported" <- c(13),
  
  "Hispanic or Latino" <- c(11),
  "Not Hispanic or Latino" <- c(59),
  "Unknown/Not Reported" <- c(2),
  
  "American Indian/Alaskan Native" <- c(0),
  "Asian/Native Hawaiian/Other Pacific Islander" <- c(5),
  "Black or African American" <- c(4),
  "White" <- c(47),
  "More Than One Race" <- c(14),
  "Unknown/Not Reported" <- c(2)
)

names(ca_demographics)[1] <- "$16,000-$24,999"
names(ca_demographics)[2] <- "$25,000-$34,999"
names(ca_demographics)[3] <- "$50,000-$74,999"
names(ca_demographics)[4] <- "$75,000-$99,999"
names(ca_demographics)[5] <- "$100,000-$199,999"
names(ca_demographics)[6] <- "Over $200,000"
names(ca_demographics)[7] <- "Unknown or Not Reported"

names(ca_demographics)[8] <- "High School/GED"
names(ca_demographics)[9] <- "Vocational"
names(ca_demographics)[10] <- "Associate degree"
names(ca_demographics)[11] <- "Bachelor's degree"
names(ca_demographics)[12] <- "Master's degree"
names(ca_demographics)[13] <- "Doctorate"
names(ca_demographics)[14] <- "Professional"
names(ca_demographics)[15] <- "Other"
names(ca_demographics)[16] <- "None of the above (less than high school)"
names(ca_demographics)[17] <- "Unknown or Not Reported"


names(ca_demographics)[18] <- "Hispanic or Latino"
names(ca_demographics)[19] <- "Not Hispanic or Latino"
names(ca_demographics)[20] <- "Unknown or Not Reported"

names(ca_demographics)[21] <- "American Indian/Alaskan Native"
names(ca_demographics)[22] <- "Asian/Native Hawaiian/Other Pacific Islander"
names(ca_demographics)[23] <- "Black or African American"
names(ca_demographics)[24] <- "White"
names(ca_demographics)[25] <- "More Than One Race"
names(ca_demographics)[26] <- "Unknown or Not Reported"


ca_demographics <- melt(ca_demographics,
                        value.name = "metric")
ca_demographics <- ca_demographics %>% rename(Variable = variable,
                                              Count = metric
)
ca_demographics$Count[17] <- 13  
ca_demographics$Count[20] <- 2
ca_demographics$Count[26] <- 2
  
ca_demographics


ca_demographics.tab <- ca_demographics %>% 
  gt() %>%
  # tab_header(
  #   title = md("**Supplementary Table 1**"),
  #   subtitle = md("*Demographic and socioeconomic information of the child/adolescent sample*")) %>%
  # tab_source_note(md("*Note.* N = 72. All information is parent/guardian reported.")) %>%
  cols_label(
    Variable = "",
    Count = "Count") %>%
  tab_row_group(
    group = "Total household income",
    rows = 1:7) %>%
  tab_row_group(
    group = "Highest degree earned by parent/guardian",
    rows = 8:17) %>%
  tab_row_group(
    group = "Ethnic categories",
    rows = 18:20) %>%
  tab_row_group(
    group = "Racial categories",
    rows = 21:26) %>%
  # tab_options(table.font.size = 20,
  #             heading.title.font.size = 20,
  #             heading.subtitle.font.size = 20,
  #             heading.align = "left",
  #             heading.border.bottom.color = 'black',
  #             table.border.top.color = "white",
  #             column_labels.border.top.color = "black",
  #             column_labels.border.bottom.color = "black",
  #             column_labels.vlines.color = "black",
  #             row_group.border.bottom.color = "black",
  #             row_group.border.top.color = "black",
  #             row_group.border.right.color = "black",
  #             stub.border.color = "black",
  #             table_body.border.bottom.color = "black",
  #             table_body.hlines.color = "black",
  #             table_body.vlines.color = "black",
  #             table.border.bottom.color = "white",
  #             table.width = pct(100),
  #             table.background.color = "white") %>%
  cols_align(align="left", columns = 1) %>%
  cols_align(align="center", columns = 2) %>%
  
  tab_style(
    style = list(
      cell_borders(
        sides = c("top", "bottom"),
        color = "white",
        weight = px(1)
      ),
      #cell_text(
      #  align="center"
      #),
      cell_fill(color = "white", alpha = NULL)
    ),
    locations = cells_body(
      columns = everything(),
      rows = everything()
    )
  ) %>%
  opt_table_font(font = google_font(name = "Times"))

# gtsave(ca_demographics.tab, file = "~/Desktop/DropBox/DEVPFC_morphology/ms/Fig_tiff/Table_1-1.rtf"
# )

ya_demographics <- data.frame(
                              "<$10,000" <- c(6),
                              "10,000-19,999" <- c(5),
                              "20,000-29,999" <- c(4),
                              "30,000-39,999" <- c(4), 
                              "40,000-49,999" <- c(2), 
                              "50,000-74,999" <- c(4),
                              "75,000-99,999" <- c(6), 
                              "Over 100,000" <- c(5),
                              
                              "<11" <- c(1),
                              "12" <- c(9),
                              "13" <- c(2), 
                              "14" <- c(2),
                              "15" <- c(2),
                              "16" <- c(13),
                              "17+" <- c(7),
                              
                              "Hispanic or Latino" <- 2,
                              "Not Hispanic or Latino" <- 33,
                              "Unknown/Not Reported" <- 1,
                              
                              "American Indian/Alaskan Native" <- 1,
                              "Asian/Native Hawaiian/Other Pacific Islander" <- 1,
                              "Black or African American" <- 7,
                              "White" <- 26,
                              "Unknown/Not Reported" <- 1
)

names(ya_demographics)[1] <- "<$10,000"
names(ya_demographics)[2] <- "$10,000-$19,999"
names(ya_demographics)[3] <- "$20,000-$29,999"
names(ya_demographics)[4] <- "$30,000-$39,999"
names(ya_demographics)[5] <- "$40,000-$49,999"
names(ya_demographics)[6] <- "$50,000-$74,999"
names(ya_demographics)[7] <- "$75,000-$99,999"
names(ya_demographics)[8] <- "Over $100,000"

names(ya_demographics)[9] <- "<11"
names(ya_demographics)[10] <- "12"
names(ya_demographics)[11] <- "13"
names(ya_demographics)[12] <- "14"
names(ya_demographics)[13] <- "15"
names(ya_demographics)[14] <- "16"
names(ya_demographics)[15] <- "<17"

names(ya_demographics)[16] <- "Hispanic or Latino"
names(ya_demographics)[17] <- "Not Hispanic or Latino"
names(ya_demographics)[18] <- "Unknown or Not Reported"

names(ya_demographics)[19] <- "American Indian/Alaskan Native"
names(ya_demographics)[20] <- "Asian/Native Hawaiian/Other Pacific Islander"
names(ya_demographics)[21] <- "Black or African American"
names(ya_demographics)[22] <- "White"
names(ya_demographics)[23] <- "Unknown or Not Reported"

ya_demographics <- melt(ya_demographics,
                  value.name = "metric")
ya_demographics <- ya_demographics %>% rename(Variable = variable,
                                              Count = metric
)

ya_demographics

ya_demographics.tab <- ya_demographics %>% 
  gt() %>%
  # tab_header(
  #   title = md("**Supplementary Table 2**"),
  #   subtitle = md("*Demographic and socioeconomic information of the young adult sample*")) %>%
  cols_label(
    Variable = "",
    Count = "Count") %>%
  # tab_source_note(md("*Note.* N = 36.")) %>%
    tab_row_group(
    group = "Total household income",
    rows = 1:8) %>%
    tab_row_group(
    group = "Years of education completed",
    rows = 9:15) %>%
    tab_row_group(
    group = "Ethnic categories",
    rows = 16:18) %>%
    tab_row_group(
    group = "Racial categories",
    rows = 19:23) %>%
  # tab_options(table.font.size = 20,
  #             heading.title.font.size = 20,
  #             heading.subtitle.font.size = 20,
  #             heading.align = "left",
  #             heading.border.bottom.color = 'black',
  #             table.border.top.color = "white",
  #             column_labels.border.top.color = "black",
  #             column_labels.border.bottom.color = "black",
  #             column_labels.vlines.color = "black",
  #             row_group.border.bottom.color = "black",
  #             row_group.border.top.color = "black",
  #             row_group.border.right.color = "black",
  #             stub.border.color = "black",
  #             table_body.border.bottom.color = "black",
  #             table_body.hlines.color = "black",
  #             table_body.vlines.color = "black",
  #             table.border.bottom.color = "white",
  #             table.width = pct(100),
  #             table.background.color = "white") %>%
  cols_align(align="left", columns = 1) %>%
  cols_align(align="center", columns = 2) %>%
  
  tab_style(
    style = list(
      cell_borders(
        sides = c("top", "bottom"),
        color = "white",
        weight = px(1)
      ),
      #cell_text(
      #  align="center"
      #),
      cell_fill(color = "white", alpha = NULL)
    ),
    locations = cells_body(
      columns = everything(),
      rows = everything()
    )
  ) %>%
  opt_table_font(font = google_font(name = "Times"))

# gtsave(ya_demographics.tab, file = "~/Desktop/DropBox/DEVPFC_morphology/ms/Fig_tiff/Table_1-2.rtf"
# )


```

##### Table 2 LPFC sulci names
```{r}
sulc_table <- data.frame("No." <- c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10",
                                    "11", "12", "13", "14", "15", "16", "17", "18"),
                               "Abbreviation" <- c("cs", "sprs", 'iprs', "ifs",
                                                   "sfs-p", "sfs-a", "imfs-h",
                                                   "imfs-v", "pmfs-p", "pmfs-i", "pmfs-a",
                                                   "pimfs+", "ds", "aalf", "ts", "half",
                                                   "prts", "lfms"),
                               "Name" <- c("central sulcus",
                                                  'superior precentral sulcus',
                                                  "inferior precentral sulcus",
                                                  "inferior frontal sulcus",
                                                  "superior frontal sulcus  posterior",
                                                  "superior frontal sulcus  anterior",
                                                  "intermediate frontal sulcus  horizontal",
                                                  "intermediate frontal sulcus  vertical",
                                                  "posterior middle frontal sulcus  posterior",
                                                  "posterior middle frontal sulcus  intermediate",
                                                  "posterior middle frontal sulcus  anterior",
                                                  "paraintermediate frontal sulcus",
                                                  "diagonal sulcus",
                                                  "ascending ramus of the lateral fissure",
                                                  "triangular sulcus",
                                                  "horizontal ramus of the lateral fissure",
                                                  "pretriangular sulcus",
                                                  "lateral frontomarginal sulcus"
                                                  )
                         )
                            

names(sulc_table)[1] <- "No."
names(sulc_table)[2] <- "Abbreviation"
names(sulc_table)[3] <- "Name"


sulc_table

sulc_table.tab <- sulc_table %>% 
  gt() %>%
  # tab_header(
  #   title = md("**Table 1**"),
  #   subtitle = md("*Sulcal definitions in lateral prefrontal cortex (LPFC)*")) %>%
  # tab_source_note(md("*Note.* Table of the 18 sulci LPFC defined in our prior work (Miller et al., 2021a,b; Voorhies et al., 2021; Yao et al., 2022). Numbers correspond to sulci in Figure 1. Sulcal abbreviations and the full name are included. +The *pimfs* can have 0, 1, or 2 components (dorsal and ventral). The *pimfs* is not included in our analyses due to its variability.")) %>%
  # tab_options(table.font.size = 20,
  #             heading.title.font.size = 20,
  #             heading.subtitle.font.size = 20,
  #             heading.align = "left",
  #             heading.border.bottom.color = 'black',
  #             table.border.top.color = "white",
  #             column_labels.border.top.color = "black",
  #             column_labels.border.bottom.color = "black",
  #             column_labels.vlines.color = "black",
  #             row_group.border.bottom.color = "black",
  #             row_group.border.top.color = "black",
  #             row_group.border.right.color = "black",
  #             stub.border.color = "black",
  #             table_body.border.bottom.color = "black",
  #             table_body.hlines.color = "black",
  #             table_body.vlines.color = "black",
  #             table.border.bottom.color = "white",
  #             table.width = pct(100),
  #             table.background.color = "white") %>%
  cols_align(align="left", columns = 1:3) %>%
  tab_style(
    style = cell_text(style = "italic"),
    locations = cells_body(
      columns = c(2),
      rows = 1:18
    )) %>%
  tab_style(
    style = list(
      cell_borders(
        sides = c("top", "bottom"),
        color = "white",
        weight = px(1)
      ),
      #cell_text(
      #  align="center"
      #),
      cell_fill(color = "white", alpha = NULL)
    ),
    locations = cells_body(
      columns = everything(),
      rows = everything()
    )
  ) %>%
  opt_table_font(font = google_font(name = "Times"))

# gtsave(sulc_table.tab, file = "~/Desktop/DropBox/DEVPFC_morphology/ms/Fig_tiff/Figure_1-1.rtf"
# )
```

##### Table 3: Depth table
```{r}
all_morph_tables_sd <- all_morph_tables_f %>% subset(metric == "depth")
all_morph_tables_sd <- all_morph_tables_sd %>% select(-c("type", "metric"))
all_morph_tables_sd <- all_morph_tables_sd[-c(8, 23), ]  

#names(all_morph_tables_sd)[1] <- "Effect"
#names(all_morph_tables_sd)[2] <- "DF1"
#names(all_morph_tables_sd)[3] <- "DF2"
names(all_morph_tables_sd)[4] <- "F-value"
names(all_morph_tables_sd)[5] <- "p-value"
names(all_morph_tables_sd)[6] <- "Significance"
names(all_morph_tables_sd)[7] <- "2G"

all_morph_tables_sd_forpaper <- all_morph_tables_sd %>% gt() %>%
  # tab_header(
  #   title = md("**Table X**"),
  #   subtitle = md("*mixed model ANOVA results for sulcal depth*")) %>%
  tab_row_group(
    group = "Normalized (% max depth)",
    rows = 15:28) %>%
  tab_row_group(
    group = "Raw (mm)",
    rows = 1:14) %>%
 tab_style(
  style = cell_text(style = "italic"),
  locations = cells_body(
 columns = c(2,4,6),
 rows = 1:6
   )) %>%
 tab_source_note(md("*Note.* N = 44. The abbreviations used are as follows: thickness at timepoint one (level); individual change from timepoint one to two (slope); standard error (Std. Err.).")) %>%
 tab_options(table.font.size = 20,
             heading.title.font.size = 20,
             heading.subtitle.font.size = 20,
             heading.align = "left",
             heading.border.bottom.color = 'black',
             table.border.top.color = "white",
             column_labels.border.top.color = "black",
             column_labels.border.bottom.color = "black",
             column_labels.vlines.color = "black",
             row_group.border.bottom.color = "black",
             row_group.border.top.color = "black",
             row_group.border.right.color = "black",
             stub.border.color = "black",
             table_body.border.bottom.color = "black",
             table_body.hlines.color = "black",
             table_body.vlines.color = "black",
             table.border.bottom.color = "white",
             table.width = pct(100),
             table.background.color = "white"
 ) %>%
  cols_align(align="center", 
             columns = 1:7) %>%
  tab_style(
    style = list(
      cell_borders(
        sides = c("top", "bottom"),
        color = "white",
        weight = px(1)
      ),
      cell_text(
        align="center"
      ),
      cell_fill(color = "white", alpha = NULL)
    ),
    locations = cells_body(
      columns = everything(),
      rows = everything()
    )
  ) %>%
  opt_table_font(font = google_font(name = "Times"))

#gtsave(all_morph_tables_sd_forpaper, file = "~/Desktop/DropBox/DEVPFC_morphology/ms/Fig_tiff/Figure_3-2.rtf")
```

##### Table 4: Surface area table
```{r}
all_morph_tables_sa <- all_morph_tables_f %>% subset(metric == "surface area")
all_morph_tables_sa <- all_morph_tables_sa %>% select(-c("type", "metric"))
all_morph_tables_sa <- all_morph_tables_sa[-c(8, 23), ]  

#names(all_morph_tables_sa)[1] <- "Effect"
#names(all_morph_tables_sa)[2] <- "DF1"
#names(all_morph_tables_sa)[3] <- "DF2"
names(all_morph_tables_sa)[4] <- "F-value"
names(all_morph_tables_sa)[5] <- "p-value"
names(all_morph_tables_sa)[6] <- "Significance"
names(all_morph_tables_sa)[7] <- "2G"

all_morph_tables_sa_forpaper <- all_morph_tables_sa %>% gt() %>%
  # tab_header(
  #   title = md("**Table X**"),
  #   subtitle = md("*mixed model ANOVA results for surface area*")) %>%
  tab_row_group(
    group = "Normalized (% cortical surface area)",
    rows = 15:28) %>%
  tab_row_group(
    group = "Raw (cm2)",
    rows = 1:14) %>%
 tab_style(
  style = cell_text(style = "italic"),
  locations = cells_body(
 columns = c(2,4,6),
 rows = 1:6
   )) %>%
 # tab_source_note(md("*Note.* N = 44. The abbreviations used are as follows: thickness at timepoint one (level); individual change from timepoint one to two (slope); standard error (Std. Err.).")) %>%
 tab_options(table.font.size = 20,
             heading.title.font.size = 20,
             heading.subtitle.font.size = 20,
             heading.align = "left",
             heading.border.bottom.color = 'black',
             table.border.top.color = "white",
             column_labels.border.top.color = "black",
             column_labels.border.bottom.color = "black",
             column_labels.vlines.color = "black",
             row_group.border.bottom.color = "black",
             row_group.border.top.color = "black",
             row_group.border.right.color = "black",
             stub.border.color = "black",
             table_body.border.bottom.color = "black",
             table_body.hlines.color = "black",
             table_body.vlines.color = "black",
             table.border.bottom.color = "white",
             table.width = pct(100),
             table.background.color = "white"
 ) %>%
  cols_align(align="center", 
             columns = 1:7) %>%
  tab_style(
    style = list(
      cell_borders(
        sides = c("top", "bottom"),
        color = "white",
        weight = px(1)
      ),
      cell_text(
        align="center"
      ),
      cell_fill(color = "white", alpha = NULL)
    ),
    locations = cells_body(
      columns = everything(),
      rows = everything()
    )
  ) %>%
  opt_table_font(font = google_font(name = "Times"))

#gtsave(all_morph_tables_sa_forpaper, file = "~/Desktop/DropBox/DEVPFC_morphology/ms/Fig_tiff/Figure_3-3.png")
```

##### Table 5: Thickness table
```{r}
all_morph_tables_ct <- all_morph_tables_f %>% subset(metric == "thickness")
all_morph_tables_ct <- all_morph_tables_ct %>% select(-c("type", "metric"))
all_morph_tables_ct <- all_morph_tables_ct[-c(8, 23), ]  

#names(all_morph_tables_ct)[1] <- "Effect"
#names(all_morph_tables_ct)[2] <- "DF1"
#names(all_morph_tables_ct)[3] <- "DF2"
names(all_morph_tables_ct)[4] <- "F-value"
names(all_morph_tables_ct)[5] <- "p-value"
names(all_morph_tables_ct)[6] <- "Significance"
names(all_morph_tables_ct)[7] <- "2G"

all_morph_tables_ct_forpaper <- all_morph_tables_ct %>% gt() %>%
  # tab_header(
  #   title = md("**Table X**"),
  #   subtitle = md("*mixed model ANOVA results for cortical thickness*")) %>%
  tab_row_group(
    group = "Normalized (% max thickness)",
    rows = 15:28) %>%
  tab_row_group(
    group = "Raw (mm)",
    rows = 1:14) %>%
 # tab_style(
  #  style = cell_text(style = "italic"),
  #  locations = cells_body(
      #columns = c(2,4,6),
      #rows = 1:6
 #   )) %>%
 # tab_source_note(md("*Note.* N = 44. The abbreviations used are as follows: thickness at timepoint one (level); individual change from timepoint one to two (slope); standard error (Std. Err.).")) %>%
  # tab_options(table.font.size = 20,
  #             heading.title.font.size = 20,
  #             heading.subtitle.font.size = 20,
  #             heading.align = "left",
  #             heading.border.bottom.color = 'black',
  #             table.border.top.color = "white",
  #             column_labels.border.top.color = "black",
  #             column_labels.border.bottom.color = "black",
  #             column_labels.vlines.color = "black",
  #             row_group.border.bottom.color = "black",
  #             row_group.border.top.color = "black",
  #             row_group.border.right.color = "black",
  #             stub.border.color = "black",
  #             table_body.border.bottom.color = "black",
  #             table_body.hlines.color = "black",
  #             table_body.vlines.color = "black",
  #             table.border.bottom.color = "white",
  #             table.width = pct(100),
  #             table.background.color = "white"
  # ) %>%
  cols_align(align="center", 
             columns = 1:7) %>%
  tab_style(
    style = list(
      cell_borders(
        sides = c("top", "bottom"),
        color = "white",
        weight = px(1)
      ),
      cell_text(
        align="center"
      ),
      cell_fill(color = "white", alpha = NULL)
    ),
    locations = cells_body(
      columns = everything(),
      rows = everything()
    )
  ) %>%
  opt_table_font(font = google_font(name = "Times"))

#gtsave(all_morph_tables_ct_forpaper, file = "~/Desktop/DropBox/DEVPFC_morphology/ms/Fig_tiff/Figure_3-4.rtf")
```
